### 2018-03-06 article/Caze_2018.tex
Fix minor typos and typographic issues

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
		Romain Cazé,
		Marcel Stimberg,
		Benoît Girard
  },
            pdftitle=
{
[Re] Non-additive coupling enables propagation of synchronous spiking activity in purely random networks
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\usepackage{siunitx}
\newcommand{\blau}[1]{{\color{blue} #1}}
\newcommand{\rot}[1]{{\color{red} #1}}

\lstnewenvironment{code}{\lstset{language=Python,basicstyle=\small\ttfamily,showstringspaces=false,stringstyle=\color{blue},commentstyle=\color{blue},columns=spaceflexible}}{}

%\usepackage{fancyvrb}
%\VerbatimFootnotes
%\usepackage{graphicx}
%\usepackage{mdframed}
%\newmdenv[backgroundcolor=lightgray]{Shaded}

\usepackage{longtable,booktabs}

\usepackage[
  backend=biber,
%  style=alphabetic,
%  citestyle=numeric
]{biblatex}
\bibliography{biblio.bib}

% --- Macros ------------------------------------------------------------------
\renewcommand*{\bibfont}{\small \sffamily}

\definecolor{red}{HTML}{CF232B}
\newcommand{\ReScience}{Re{\bfseries \textcolor{red}{Science}}}

\newtcolorbox{rebox}
   {colback=blue!5!white, colframe=blue!40!white,
     boxrule=0.5pt, arc=2pt, fonttitle=\sffamily\scshape\bfseries,
     left=6pt, right=20pt, top=6pt, bottom=6pt}

\newtcolorbox{repobox}
   {colback=red, colframe=red!75!black,
     boxrule=0.5pt, arc=2pt, left=6pt, right=6pt, top=3pt, bottom=3pt}

% fix for pandoc 1.14     
\newcommand{\tightlist}{%
  \setlength{\itemsep}{1pt}\setlength{\parskip}{0pt}\setlength{\parsep}{0pt}}

% --- Style -------------------------------------------------------------------
\renewcommand*{\bibfont}{\small \sffamily}
\renewcommand{\captionfont}{\small\sffamily}
\renewcommand{\captionlabelfont}{\bfseries}

\makeatletter
\renewcommand\@biblabel[1]{{\bf #1.}}
\makeatother

% --- Page layout -------------------------------------------------------------
\usepackage[top=3.5cm, bottom=3cm, right=1.5cm, left=1.5cm,
            headheight=2.2cm, reversemp, includemp, marginparwidth=4.5cm]{geometry}

% --- Section/SubSection/SubSubSection ----------------------------------------
\titleformat{\section}
  {\normalfont\sffamily\Large\bfseries}
  {}{0pt}{}
\titleformat{\subsection}
  {\normalfont\sffamily\large\bfseries}
  {}{0pt}{}
\titleformat{\subsubsection}
  {\normalfont\sffamily\bfseries}
  {}{0pt}{}
\titleformat*{\paragraph}
  {\sffamily\normalsize}

% --- Header / Footer ---------------------------------------------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
%\renewcommand{\headrulewidth}{0.50pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\hspace{-1cm}\includegraphics[width=4.0cm]{rescience-logo.pdf}}
\fancyhead[C]{}
\fancyhead[R]{} 
\renewcommand{\footrulewidth}{0.25pt}

\fancyfoot[L]{\hypersetup{urlcolor=red}
              \sffamily \ReScience~$\vert$
              \href{http://rescience.github.io}{rescience.github.io}
              \hypersetup{urlcolor=blue}}
\fancyfoot[C]{\sffamily 1 - \thepage}
\fancyfoot[R]{\sffamily Jan 2018 $\vert$
                        Volume \textbf{1} $\vert$
                        Issue \textbf{1}}
\pagestyle{fancy}
\makeatletter
\let\ps@plain\ps@fancy
\fancyheadoffset[L]{4.5cm}
\fancyfootoffset[L]{4.5cm}

% --- Title / Authors ---------------------------------------------------------
% patch \maketitle so that it doesn't center
\patchcmd{\@maketitle}{center}{flushleft}{}{}
\patchcmd{\@maketitle}{center}{flushleft}{}{}
% patch \maketitle so that the font size for the title is normal
\patchcmd{\@maketitle}{\LARGE}{\LARGE\sffamily}{}{}
% patch the patch by authblk so that the author block is flush left
\def\maketitle{{%
  \renewenvironment{tabular}[2][]
    {\begin{flushleft}}
    {\end{flushleft}}
  \AB@maketitle}}
\makeatletter
\renewcommand\AB@affilsepx{ \protect\Affilfont}
%\renewcommand\AB@affilnote[1]{{\bfseries #1}\hspace{2pt}}
\renewcommand\AB@affilnote[1]{{\bfseries #1}\hspace{3pt}}
\makeatother
\renewcommand\Authfont{\sffamily\bfseries}
\renewcommand\Affilfont{\sffamily\small\mdseries}
\setlength{\affilsep}{1em}

\LetLtxMacro{\OldIncludegraphics}{\includegraphics}
\renewcommand{\includegraphics}[2][]{\OldIncludegraphics[width=12cm, #1]{#2}}

% --- Document ----------------------------------------------------------------
\title{[Re] Non-additive coupling enables propagation of synchronous spiking activity in purely random networks}

\usepackage{authblk}
                \author[1]{Romain Cazé}
                \author[2]{Marcel Stimberg}
                \author[1]{Benoît Girard}
                \affil[1]{Sorbonne Université, ISIR \'equipe AMAC, Paris, France}
                \affil[2]{Sorbonne Université, INSERM, CNRS, Institut de la Vision, Paris, France}

\date{\vspace{-5mm}
      \sffamily \small \href{mailto:romain.caze@upmc.fr}{romain.caze@upmc.fr}}

\setlength\LTleft{0pt}
\setlength\LTright{0pt}

% --- Additional packages ----
% Package for subfigures
\usepackage[position=top,labelformat=simple,labelfont=bf]{subcaption}
\renewcommand*{\thesubfigure}{\Alph{subfigure}} % Upper case letters for subfigures

%% Useful packages
\usepackage{amsmath}
\usepackage[colorinlistoftodos]{todonotes}

\begin{document}
\maketitle

\marginpar{
  %\hrule
  \sffamily\small
  %\vspace{2mm}
  {\bfseries Editor}\\
  Name Surname\\

  {\bfseries Reviewers}\\
        Name Surname\\
        Name Surname\\

  {\bfseries Received}  Month, day, year\\
  {\bfseries Accepted}  Month, day, year\\
  {\bfseries Published} Month, day, year\\

  {\bfseries Licence}   \href{http://creativecommons.org/licenses/by/4.0/}{CC-BY}

  \begin{flushleft}
  {\bfseries Competing Interests:}\\
  The authors have declared that no competing interests exist.
  \end{flushleft}

  \hrule
  \vspace{3mm}

  \hypersetup{urlcolor=white}

    \vspace{-1mm}
  \begin{repobox}
    \bfseries\normalsize
      \href{http://github.com/rescience/rescience-submission/article}{\faGithubAlt~Article repository}
  \end{repobox}
      \vspace{-1mm}
  \begin{repobox}
    \bfseries\normalsize
      \href{http://github.com/rescience/rescience-submission/code}{\faGithubAlt~Code repository}
  \end{repobox}
        \hypersetup{urlcolor=blue}
}

\begin{rebox}
\sffamily {\bfseries A reference implementation of}
\small
\begin{flushleft}
\begin{itemize}
    \item[→] Non-additive coupling enables propagation of synchronous spiking activity in purely random networks, R.M. Memmesheimer, M. Timme, PLoS Computational Biology, 8(4): e1002384, 2012. DOI: 10.1371/journal.pcbi.1002384
  \end{itemize}\par
\end{flushleft}
\end{rebox}

\section*{Introduction}
Dendritic non-linearities increase neurons' computation capacity, turning them into complex computing units \cite{Poirazi2003a}. However network studies are usually based on point neuron models that do not incorporate dendrites and their non-linearities. In contrast, the study replicated here \cite{Memmesheimer2012} uses a simple point-neuron model that contains an effective description of dendrites by a non-linear summation of its excitatory synaptic input. Due to the simplicity of the model, both large-scale parameter exploration of a medium-sized network, as well as an analytical investigation of its properties are feasible.

The original study was based on simulation and analysis code in C and Mathematica, but this code is not publicly available. Here, we replicate the study using the neural simulator Brian~2 \cite{Goodman2009,Stimberg2014}, a simulator based on the Python language that has become a common choice in computational neuroscience \cite{Muller2015}. This simulator offers a good trade-off between flexibility and performance and is therefore a suitable choice for this study of a non-standard neuron model.

\section*{Methods}
\subsection*{Neural network model}
The simulations in the original paper were done in phase representation, but our implementation uses the more standard representation in terms of the neurons' membrane potential. The membrane potential $V_i$ (measured relative to the resting potential) of neuron $i$ is described by (a slightly rewritten version equivalent to equation (1) of \cite{Memmesheimer2012}):

\begin{equation}
\tau_m \frac{dV_i(t)}{dt} = - V_i(t) + V_0 + \sigma \left( \sum_{j\in E_i} w_\text{ex} \epsilon_{j}(t-\tau) \right) - \sum_{j \in I_i} w_\text{in}\epsilon_{j}(t-\tau),
\end{equation}
where $V(t)$ is the membrane voltage at time $t$, $\tau_m$ the membrane time constant, $V_0$ the displacement of the membrane potential due to a constant external input, $w_\text{ex}$ and $w_\text{in}$ respectively the excitatory and inhibitory weights, $\tau$ the transmission delay, and $E_i$ and $I_i$ the indices of neurons that connect with respectively excitatory and inhibitory weights to neuron $i$. If the membrane potential crosses a threshold $\Theta$, it emits the spike and its membrane potential is reset to its resting potential, i.e. $\SI{0}{\milli\volt}$. The function $\epsilon_{j}$ is 1 whenever neuron $j$ spikes, and 0 otherwise.

The originality of this model lays in a filtering of the excitatory inputs by the function $\sigma$ to model dendritic non-linearities. The study considers two functions $\sigma$ (see Fig.~1 of the original paper and insets in Fig.~\ref{fig:markov}). Linear coupling, defined by $\sigma(x)=x$, and non-linear coupling with:
\begin{equation}
    \sigma(x)= 
\begin{cases}
    x              & \text{, if } x\leq V_a\\
    V_a + \frac{V_c-V_a}{V_b-V_a} (x - V_a), & \text{, if } V_a<x \leq V_b\\
    V_c            & \text{, otherwise.}
\end{cases}
\end{equation}
For this non-linear function, the biological interpretation is that below a first threshold $V_a$, excitatory inputs are propagated passively by the dendrite and sum linearly. Above this threshold, they trigger a dendritic spike, resulting in an amplified somatic voltage. If they are even higher and cross the threshold $V_b$, they stop increasing the somatic voltage and saturate. Note that this non-linearity only affects spikes received synchronously as has been observed experimentally. With the introduction of this non-linearity, the modelled point neuron becomes an effective model of a neuron with one non-linear dendrite.

The network consists of $N$ neurons, where a directed synaptic connection between a pair of neurons is established with probability $p_0$. Each of these connections is taken to be excitatory with probability $p_\text{ex}$, and inhibitory otherwise. Note that this connection scheme implies that neurons cannot be separated into groups of excitatory and inhibitory neurons, a neuron typically projects with both excitatory and inhibitory connections to other neurons.

The parameter values used in the original study as well as in our replication are summarized in Table~\ref{tab:parameters}.

\begin{table}[ht]
\begin{tabular}{ l  c  S p{2.85cm}}
  \toprule
  {Parameter} & {Symbol} & {Value} &\\
  \midrule
  Number of neurons & $N$ & 1000 &\\
  Connection probability & $p_0$ & 0.3 &\\
  Probability connection being excitatory & $p_\text{ex}$ & 0.5 &\\
  Excitatory connection weight & $w_\text{ex}$ & \SI{0.2}{\milli\volt} & (varied in Fig.~\ref{fig:grid})\\
  Inhibitory connection weight & $w_\text{in}$ & \SI{0.2}{\milli\volt} & (varied in Fig.~\ref{fig:grid})\\
  Membrane time constant & $ \tau_m $ & \SI{8}{\milli\second} &\\
  Firing threshold & $\Theta$ & \SI{16}{\milli\volt} &\\
  Synaptic delay & $\tau$ & \SI{5}{\milli\second} & (but see Implementation section)\\
  Threshold for supra-linear summation & $V_a$ & \SI{2}{\milli\volt} \\
  Threshold for saturation & $V_b$ & \SI{4}{\milli\volt} \\
  Saturation value & $V_c$ & \SI{6}{\milli\volt} \\
  \bottomrule
\end{tabular}
\caption{Parameter values used in the simulations}\label{tab:parameters}
\end{table}

\subsection*{Implementation and numerical methods}
The authors of the original study provided us with the principal C and Mathematica code used in their study. However, this code does not compile and run any more with recent Mathematica versions. Our implementation is not based on this code, but only on the descriptions in the original paper (with minor clarifications provided by the authors where necessary).

The authors of the original study used an event-based simulation scheme, exploiting the linearity of the sub-threshold dynamics. Due to this linearity, the membrane potential can be advanced for arbitrarily large time spans between spikes, and spike times do not have to be bound to any temporal grid. In contrast, the Brian simulator is built on a clock-driven paradigm where time is advanced in discrete steps. This is because the simulator supports a wide range of neural models of and event-driven methods can only be applied to a small number of simple neuron models, and also becomes computationally demanding in large networks with many spikes.

All simulations presented here have been performed with a step size of \SI{0.1}{\milli\second} and the forward Euler integration algorithm (changing to an exact integration based on the analytical solution of the linear equations did not change the results).

Note that the event-based method used in the original study has important consequences for the specific implementation of non-linear synaptic summation: only spikes that arrive exactly synchronously can sum up non-linearly. This, together with the synaptic delay that is constant over all connections, implies that the non-linearity will only apply to spikes that originate from neurons that spiked perfectly synchronously one synaptic delay earlier; randomly occurring spikes have only an infinitesimally small chance to arrive at the receiving neuron synchronously. When using a clock-driven algorithm, as we do in this replication, this is no longer the case. All neurons that spike within the same time step will deliver their spikes to their target neurons at the same time step, potentially triggering non-linear summation. While the clock-driven method is a less accurate method in general, we would argue that in the context of non-linear summation it is actually closer to the biological phenomenon it models. While dendrites detect synchronous events with sub-millisecond precision \cite{Softky1994}, this precision is of course finite. With that said, the qualitative results of the original study can be replicated with a clock-driven method, as we will show in the Results section.

For linearly coupled networks, the neuron model is a standard leaky-integrate-and-fire neuron with ``delta synapses'', i.e. incoming synaptic events instantaneously affect the membrane potential as soon as they are received. In Brian, this model is described as follows (omitting the code to connect the synapses and set their weights):
\begin{code}
eq = "dV/dt = -gamma*V + V0 : volt"
G = br2.NeuronGroup(N, model=eq, threshold="V>Theta",
                    reset="V=0*mV", method='euler')
exc_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='V += w', delay=5 * ms - dt)
inh_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='V -= w', delay=5 * ms - dt)
\end{code}
Note that the delay has been set as one time step (\verb|dt|) less than \SI{5}{\milli\second}. This is because in Brian, when a neuron receives synaptic input, this input can only trigger a threshold crossing of the receiving neuron in the following time step. To get chains of propagated synchronous spikes every \SI{5}{\milli\second} as in the original study, we therefore have to reduce the delay by one time step.

For non-linearly coupled networks, we have to use a slightly more complicated approach where we sum up all the received excitatory input in a variable \verb|ve|, apply the non-linear function $\sigma$ to this input, and then reset the variable \verb|ve| back to 0 to prepare for the next time step. In Brian syntax (the definition of the inhibitory synapses is identical to the linearly coupled network):
\begin{code}
eq = """dV/dt = -gamma*V + V0 : volt
        ve : volt
     """
G = br2.NeuronGroup(N, model=eq, threshold="V>Theta",
                    reset="V=0*mV", method='euler')
exc_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='ve += w', delay=5 * ms - dt)
G.run_regularly('''
                V += clip(ve, 0*mV, 2*mV) + clip(2*(ve-2*mV), 0*mV, 4*mV)
                ve = 0*mV
                ''', when='after_synapses')
\end{code}
The \verb|run_regularly| operation that is run every time step to implement the non-linear $\sigma$ function refers to the predefined \verb|clip| function which clips the value to a given range, following the syntax
\begin{code}
clip(value, lower_bound, upper_bound)
\end{code}
To facilitate simulation, we use the \emph{joblib} library to automatically store results and to distribute computation over processor cores. Several simulation and analysis functions are annotated with a \verb|@mem.cache| decorator, meaning that their input arguments and outputs will be automatically stored to disk and calling the function will return the stored values if available. This feature does not only ease development (e.g. plotting functions can be changed without re-running the underlying simulations), but also allows to interrupt long-running parameter explorations without losing the results obtained so far. The same result could be achieved by manually storing results to disk, but joblib's caching mechanism helps to avoid common errors (e.g. to re-use an old result obtained with an outdated version of the code) while keeping the code readable. To reduce the total simulation time, the grid exploration in Fig.~\ref{fig:grid}, and the analysis of group size evolution in Fig.~\ref{fig:markov} have been distributed over processor cores using joblib's \verb|Parallel| construct. For the simulations presented in Fig.~\ref{fig:grid}, multiple repetitions for the same combination of synaptic weights are distributed over processor cores, for the simulations presented in Fig.~\ref{fig:markov}, simulations are evaluated in parallel over group sizes. In both cases, a number of $C-1$ parallel processes is used, where $C$ is the number of processor cores in the user's system.

We wanted reproducible simulations despite the use of random connectivity and initial conditions. Setting a single global seed was not sufficient because we used parallel simulations executed in non-deterministic order. Instead, we used a set of pre-determined seeds, one for each figure, and used those ``meta-seeds'' to generate a set of random seeds for each individual simulation.

For the grid search presented in Fig.~\ref{fig:grid}, we varied inhibitory and excitatory synaptic weights between \SI{0.16}{\milli\volt} and \SI{0.4}{\milli\volt} (given that each neuron receives on average 150 excitatory and 150 inhibitory inputs, this corresponds to a ``total weight'' between \SI{24}{\milli\volt} and \SI{60}{\milli\volt}, as used on the axes of Fig.~\ref{fig:grid}), using 100 steps for each variable (comparable to the 96 steps used in the original publication). Each network was simulated 10 times with different initial conditions (synaptic connections and initial membrane potential values), whereas the original publication used 20 simulations per weight combination and additionally added ``1--50 random spikes initially in transit''.

To numerically derive the evolution of synchronous pulse sizes presented in Fig.~\ref{fig:markov} (for the semi-analytical approach, see the next section), we performed simulations of \SI{56}{\milli\second} each. During each simulation, we stimulated the network at \SI{50}{\milli\second} with a synchronous pulse of activity, consisting of between 1 and 176 neurons (varied in steps of 5 -- the original study used group sizes between 1 and 181 varied in steps of 6). We then observed the number of active neurons at \SI{55}{\milli\second}, i.e. at one $\tau$ after the stimulation. For each stimulation group size, we ran the simulations 50~times with different initial conditions, consistent with the original study.

\subsection*{Semi-analytical and analytical methods}
We did not attempt to replicate the analytical solution for the evolution of synchronous pulses based on diffusion approximation (blue dots in Fig.~4 of \cite{Memmesheimer2012}).
To calculate the semi-analytical solutions for Fig.~\ref{fig:markov}, based on a numerical estimate of the distribution $P(V)$, we proceeded as follows. First, we ran $2\times 50$ (once for the linear, once for the non-linear network) simulations of \SI{250}{\milli\second} each of a network with the default parameters but without any additional synchronous stimulation.  We binned all membrane potential values over all time steps and neurons into 100 bins in the voltage interval $[-\Theta/8, \Theta]$, to obtain an estimate of $P(V)$, the distribution of the membrane potential. From this distribution we can estimate the probability $F$ that an additional input $\epsilon$ drives the neuron over its threshold (or equivalently, that the neuron is less than $\epsilon$ away from its threshold):
\begin{equation}
F(\epsilon) = P(V>\Theta-\epsilon) = \int_{\Theta-\epsilon}^{\Theta}P(V)dV
\end{equation}
Let $\epsilon(n_\text{ex}, n_\text{in})$ be the total input to a neuron that receives $n_\text{ex}$ excitatory and $n_\text{in}$ inhibitory spikes, i.e. $\epsilon(n_\text{ex}, n_\text{in}) = \sigma(n_\text{ex}w_\text{ex}) + n_\text{in}w_\text{in}$. Let us assume that in the last iteration $g_i$ neurons spiked and that these neurons are refractory now, i.e. that $N-g_i$ neurons are available to spike in this iteration. To calculate the probability for a single (non-refractory) neuron $j$ to spike in response to these $g_i$ neurons, we will first calculate the probability that out of the $g_i$ neurons that spiked, exactly $n_\text{ex}$ neurons are connected with excitatory connections and $n_\text{in}$ neurons are connected with inhibitory connections to neuron $j$. There are $\binom{g_i}{n_\text{ex} + n_\text{in}}$ possibilities to chose $n_\text{ex} + n_\text{in}$ out of $g_i$ neurons, and $\binom{n_\text{ex} + n_\text{in}}{n_\text{ex}}$ possibilities to divide these neurons into groups of size $n_\text{ex}$ and $n_\text{in}$. This yields the total number of combinations $c(g_i, n_\text{ex}, n_\text{in})$:
\begin{equation}
c(g_i, n_\text{ex}, n_\text{in}) = \binom{g_i}{n_\text{ex} + n_\text{in}}\binom{n_\text{ex} + n_\text{in}}{n_\text{ex}} = \frac{g_i!}{n_\text{ex}!n_\text{in}!(g_i - n_\text{ex} - n_\text{in})!}
\end{equation}
The probability that these selected $n_\text{ex}$ neurons are actually connected via excitatory connections to neuron $j$, that the $n_\text{in}$ neurons are actually connected via inhibitory connections to neuron $j$, and that the remaining $g_i - n_\text{ex} - n_\text{in}$ neurons are \emph{not} connected to neuron $j$ is:
\begin{equation}
p(g_i, n_\text{ex}, n_\text{in}) = (p_0 p_\text{ex})^{n_\text{ex}} (p_0 p_\text{in})^{n_\text{in}} (1 - p_0)^{g_i - n_\text{ex} - n_\text{in}}
\end{equation}
Finally, we need to sum these probabilities up over all possible values for $n_\text{ex}$ and $n_\text{in}$, multiplying it with the probability that the generated input elicits a spike. This yiels the total probability $P^s(g_i)$ that a neuron $j$ spikes in response to the activity of $g_i$ neurons in the previous iteration:
\begin{equation}
P^s(g_i) = \sum_{n_\text{ex}=1}^{g_i}\sum_{n_\text{in}=0}^{g_i-n_\text{ex}} F\big(\epsilon(n_\text{ex}, n_\text{in})\big) c(g_i, n_\text{ex}, n_\text{in}) p(g_i, n_\text{ex}, n_\text{in})
\end{equation}
In Fig.~\ref{fig:markov}, we plot the expected value of spiking neurons during the next iteration, i.e.:
\begin{equation}
E(g_{i+1}|g_i = g_i') = (N - g_i') P^s(g_i')
\end{equation}

\section*{Results}
\begin{figure}
\centering
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/spikes_l_dt_100us.pdf}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/spikes_nl_dt_100us.pdf}
\end{subfigure}
\caption{\label{fig:raster}
\textbf{Propagation of synchronous spiking in linearly (A) and non-linearly (B) coupled networks.} We initiate a chain of synchronous pulses by applying external supra-threshold inputs to the first 100 neurons at time $t=\SI{150}{\milli\second}$ (red coloured spikes, grey vertical dotted lines indicate times where spikes occur as part of the chain). Top row: total size $g'$ of synchronized groups within the chain. Middle row: network rate over all neurons (rate in \si{\kilo\hertz}, bin size \SI{1}{\milli\second}). Bottom row: spiking activity of the first 200 neurons in a network of a 1000 neurons versus time.\\
Replication of Fig.~2 in \cite{Memmesheimer2012} (\url{https://doi.org/10.1371/journal.pcbi.1002384.g002}).}
\end{figure}

We first replicate a simulation showing the propagation of synchronous spiking activity in networks using linear (Fig.~\ref{fig:raster}A) and non-linear (Fig.~\ref{fig:raster}B) coupling. This figure corresponds to Fig.~2 of the original article. Given that the simulations are based on random synaptic connections and random initial conditions, we do not expect exact replication of spike times, but the qualitative features of the simulation are faithfully replicated: synchronous activity quickly dies out and disappears in the background activity for linearly coupled networks (Fig.~\ref{fig:raster}A) but is persistently propagated in non-linearly coupled networks (Fig.~\ref{fig:raster}B).

To confirm the equivalence of our network's behaviour with the original study over a wide range of synaptic connection strength we ran a grid search exploration for linearly (Fig.~\ref{fig:grid}A) and non-linearly (Fig.~\ref{fig:grid}B) coupled networks. Network behaviour is colour-coded as being part of one out of four classes: stable activity, but no persistent propagation (green); stable activity with persistent propagation (blue); unstable activity after synchronous stimulation (yellow); unstable activity before synchronous stimulation (red). For quantitative definitions, see Table~\ref{tab:color}. We run each combination of connection strengths 10 times, and combine the results to yield a color in RGB notation (values between 0 and 1 for the red, green, and blue component), according to:
\begin{equation}
R = U_1 + U_2;\quad G = E + U_2;\quad B = S,
\end{equation}
where $U_1$, and $U_2$ stand for the fraction of trials displaying unstable network activity before respectively after onset of propagation, and $S$ and $E$ for the fraction of trials displaying stable background activity with respectively without persistent propagation. We obtained this scheme directly from the authors of the original study, it was only coarsely described in the original publication. Combining individual results in this way does not necessarily lead to easily interpretable colours, but using a different scheme, e.g. colouring according to the class that occurred the most often, leads to visually similar results (not shown).

Our replication does not reproduce all details of the original plots (in particular at the top of the plots), but looks very similar on a coarse scale. Importantly, it strongly supports the original paper's main conclusion that non-linearly coupled networks have a large parameter range of stable propagation (i.e., blue-coloured points), while linearly coupled networks do not. The minor differences in our replication could be due to either our use of a clock-based simulation method, or to the slightly different initial conditions (no spikes ``in transit'').
\begin{table}
\begin{tabular}{ c  l  p{0.32\textwidth}}
  \toprule
   & Class & Definition \\
  \midrule
  $U_1$ (red) & Unstable before stimulation & $\exists t<t_\text{stim}: a_b(t) \geq 100$ \\
  $U_2$ (yellow) & Unstable after stimulation & $\exists t>t_\text{stim}: a_b(t) \geq 100$ \\
  $E$ (green) &  Stable activity, no propagation & $\forall t: a_b(t) < 100\, \wedge\, g_\text{p} < 10$\\
  $S$ (blue) & Stable activity, persistent propagation & $\forall t: a_b(t) < 100\, \wedge\, g_\text{p} \geq 10$\\
  \bottomrule
\end{tabular}
\caption{Classification of network behaviour for Fig.~\ref{fig:grid}. Here, $a_b$ refers to the background activity, the number of neurons active during a \SI{1}{\milli\second} time bin, ignoring the time steps at $t_\text{p}^k = t_\text{stim} + k\cdot\tau$, i.e. time steps that follow the synchronous stimulation by multiples of the synaptic delay. The variable $g_\text{p}$ refers to the number of successful propagations of the synchronous activity, i.e. the number of time steps $t_\text{p}^k$ where the number of active neurons exceeds the maximal background activity $a_b$.}\label{tab:color}
\end{table}

\begin{figure}
\centering
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/grid_l_dt_100us_mean.pdf}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_mean.pdf}
\end{subfigure}
\caption{\label{fig:grid}
\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for linearly (A) and non-linearly (B) coupled networks.} For each combination, we initiated synchronous activity with 100 neurons and assessed the stability of the temporal evolution. Blue colouring indicates stable propagation of synchrony, red indicates unstable background activity before onset of propagation, yellow indicates unstable background activity after onset of propagation, and green colouring indicates the absence of propagation (see Methods for details).\\
Replication of Fig.~3a and b in \cite{Memmesheimer2012} (\url{https://doi.org/10.1371/journal.pcbi.1002384.g003})}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/markov_l_dt_100us.pdf}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/markov_nl_dt_100us.pdf}
\end{subfigure}
\caption{\label{fig:markov}
\textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks.} To numerically estimate the probability distribution, we show occurrences of pulse-sizes $g'_1$ in response to a pulse of size $g'_0$ by grey lines; green squares represent the corresponding mean response group sizes.\\
Replication of Fig.~4 in \cite{Memmesheimer2012} (\url{https://doi.org/10.1371/journal.pcbi.1002384.g004})}
\end{figure}

Finally, we looked at the evolution of synchronous group sizes for one combination of synaptic weights ($w_\text{ex}=w_\text{in}=\SI{0.2}{\milli\volt}$) in detail (Fig.~\ref{fig:markov}). The results confirms our previous conclusion that we can faithfully replicate the network behaviour. They match both qualitatively and quantitatively, the group size consistently declines with each iteration in linearly coupled networks (Fig.~\ref{fig:markov}A), whereas it increases for intermediate group sizes and declines otherwise in non-linearly coupled networks (Fig.~\ref{fig:markov}B). While the semi-analytic solution (red dotted line) shows a good match to the numerical results (grey lines, means as green dots), it shows some quantitative differences to the semi-analytic solution presented in Fig.~4 of the original article. In particular, our semi-analytical solution seems to mostly slightly underestimate the size of the group in the next iteration while the semi-analytical solution presented in the original article seems to slightly overestimate it.

\section*{Discussion}

We managed to qualitatively reproduce the main results of Raoul-Martin Memmes\-heimer and Marc Timme \cite{Memmesheimer2012} despite some slight quantitative differences. These difference could be due to our use of clock-based instead of event-driven simulations, as it forces all activity to a temporal grid of finite precision. We tried finer (\SI{0.05}{\milli\second}) and coarser (\SI{0.2}{\milli\second}, \SI{0.5}{\milli\second}) temporal resolutions and obtained qualitatively the same results (not shown). Another potential source for the differences is that our initial conditions do not include spikes ``in transit'' at the start of the simulation, which might further contribute to the quantitative differences we see.

The reusable code we provide with this work paves the way to future studies of networks of non-linearly coupled integrate-and-fire neurons. It gives researchers the means to verify that the original study's conclusion hold under variations of its model assumptions, such as the details of the connectivity scheme or the synaptic model. This article has already provided a first such verification, demonstrating that the original studies main findings do not critically depend on the event-based method and the entailing ``perfect time resolution''. Finally, we hope that the provided code can also serve as a basis for future studies of functional paradigms going beyond the mere propagation of synchronous activity.

\section*{Acknowledgements}
We would like to thank Raoul Martin Memmesheimer for providing implementation details about the original study. This work has received funding from the European Union’s Horizon 2020 research and innovation programme under grant agreement No 640891 (DREAM Project).

{\sffamily \small
   \printbibliography[title=References]
%}

\end{document}

### 2018-03-06 article/Caze_2018.tex
Add V_0 to the parameter table

@@
   Firing threshold & $\Theta$ & \SI{16}{\milli\volt} &\\
+  External input & $V_0$ & \SI{17.6}{\milli\volt}&(effect on $V$)\\
   Synaptic delay & $\tau$ & \SI{5}{\milli\second} & (but see Implementation section)\\

### 2018-03-06 code/lib.py
Introducing a global variable GROUP_SIZE to generate the third panel

@@ -1,7 +1,6 @@
 from __future__ import print_function, division
 
 from collections import Counter
-from math import factorial
 
 import numpy as np
 from scipy.special import comb
@@ -11,9 +10,12 @@ import brian2 as br2
 from brian2 import mV, ms
 
 mem = Memory(cachedir='./__joblib_cache__', verbose=0, compress=True)
+# Introduce a global variable setting the group size
+GROUP_SIZE = 100
 
 
-def group_size_evolutions(group_size, n_rep=1, linear=True, dt=0.1*ms, seeds=None):
+def group_size_evolutions(group_size, n_rep=1, linear=True, dt=0.1*ms,
+                          seeds=None):
     """Return the evolution of the group size after one cycle"""
     group_ev = []
     for rep in range(n_rep):
@@ -21,27 +23,33 @@ def group_size_evolutions(group_size, n_rep=1, linear=True, dt=0.1*ms, seeds=Non
             seed = None
         else:
             seed = seeds[rep]
-        results = run_with_cache(56 * ms, group_size=group_size, stim_time=50 * ms,
-                                 linear=linear, repetition=rep, dt=dt, seed=seed)
+        results = run_with_cache(56 * ms, group_size=group_size,
+                                 stim_time=50 * ms, linear=linear,
+                                 repetition=rep, dt=dt, seed=seed)
         group_ev.append(np.sum(np.abs(results['t'] - 55 * ms) < dt / 2))
     return group_ev
+
 
 def F(bins, v_hist, epsilon):
     """Probability that an input of strength epsilon elicits a spike."""
     theta = bins[-1]
-    return np.sum(v_hist[bins[:-1]>theta-epsilon/mV])
+    return np.sum(v_hist[bins[:-1] > theta-epsilon/mV])
+
 
 def epsilon(n_ex, n_in, w_ex, w_in, linear=True):
     in_input = -n_in*w_in
     ex_input = n_ex*w_ex
     if not linear:
-        ex_input = np.clip(ex_input, 0*mV, 2*mV) + np.clip(2*(ex_input-2*mV), 0*mV, 4*mV)
+        ex_input = np.clip(ex_input, 0*mV, 2*mV) + np.clip(2*(ex_input-2*mV),
+                                                           0*mV, 4*mV)
     return in_input + ex_input
+
 
[…]

### 2018-03-06 code/main.py

@@ -9,6 +9,8 @@ from brian2 import mV, us, ms
 from joblib import Parallel, delayed
 import matplotlib.pyplot as plt
 
+# Adding the line below to modify GROUP_SIZE
+import lib
 from lib import run_with_cache, group_size_evolutions, calc_group_evolution_cached, decide_color, grid_search
 from plot import plot_population_activity, plot_markov, plot_grid
 
@@ -38,8 +40,10 @@ def fig2(quiet=False, dt=0.1*ms, seed=None):
     if not quiet:
         print('Running simulations for Figure 2')
     seeds = generate_seeds(seed, 2)
-    results = run_with_cache(w_ex=0.2*mV, w_in=0.2*mV, linear=True, dt=dt, seed=seeds[0])
-    results_nl = run_with_cache(w_ex=0.2*mV, w_in=0.2*mV, linear=False, dt=dt, seed=seeds[1])
+    results = run_with_cache(w_ex=0.2*mV, w_in=0.2*mV, linear=True, dt=dt,
+                             seed=seeds[0])
+    results_nl = run_with_cache(w_ex=0.2*mV, w_in=0.2*mV, linear=False, dt=dt,
+                                seed=seeds[1])
 
     figname = "spikes_l_dt_%.0fus.pdf" % (dt/us)
     plot_population_activity(results, save=FIG_FOLDER + figname, dt=dt)
@@ -47,17 +51,19 @@ def fig2(quiet=False, dt=0.1*ms, seed=None):
     plot_population_activity(results_nl, save=FIG_FOLDER + figname, dt=dt)
 
 
-def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None):
+def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
+         group_size=100):
     """Perform a grid search over the excitatory and inhibitory coupling
     strengths and generate Figures 3a and 3b of the original paper
     (https://doi.org/10.1371/journal.pcbi.1002384.g003)"""
     if not quiet:
         print('Running simulations for Figure 3 ({} '
-              'coupling)'.format('linear' if linear else 'nonlinear'))
+              'coupling) with group_size {}'.format('linear' if linear else 'nonlinear',
+                                              group_size))
 
     if short:
         par_range = np.linspace(0.16, 0.4, 10, endpoint=True)*mV
-        repetitions = 5
+        repetitions = 1
         name = "grid_short"
[…]

### 2018-03-06 article/Caze_2018.tex
Rewrite the description of the differences in the semi-analytical solution

@@
 While the semi-analytic solution (red dotted line) shows a good match to the numerical results (grey lines, means as green dots), it shows some quantitative differences to the semi-analytic solution presented in Fig.~4 of the original article.
-In particular, our semi-analytical solution seems to mostly slightly underestimate the size of the group in the next iteration while the semi-analytical solution presented in the original article seems to slightly overestimate it.
+The semi-analytical solution in the original article consistently overestimates the size of the group in the next iteration compared to the numerical solution.
+In contrast, our semi-analytical solution consistently underestimates their size in linearly coupled networks (Fig.~\ref{fig:markov}A).
+For non-linearly coupled networks, our solution underestimates the evolution of the group size for initial group sizes up to about 115--125 and only overestimates it for higher initial group sizes.
 

### 2018-03-06 code/lib.py
Litter the code with group_size=group_size ;)

@@ -10,8 +10,6 @@ import brian2 as br2
 from brian2 import mV, ms
 
 mem = Memory(cachedir='./__joblib_cache__', verbose=0, compress=True)
-# Introduce a global variable setting the group size
-GROUP_SIZE = 100
 
 
 def group_size_evolutions(group_size, n_rep=1, linear=True, dt=0.1*ms,
@@ -69,7 +67,7 @@ calc_group_evolution_cached = mem.cache(calc_group_evolution)
 
 def run(runtime=250*ms, stim_time=150*ms, N=1000,
         linear=True, w_ex=0.2*mV, w_in=0.2*mV, repetition=0,
-        store_spikes=True, store_v=False, dt=0.1*ms, seed=None):
+        store_spikes=True, store_v=False, dt=0.1*ms, seed=None, group_size=100):
     """Run a simulation and return the resulting spiketrain.
 
     Note: the `repetition` argument is only used to distinguish multiple runs
@@ -105,7 +103,7 @@ def run(runtime=250*ms, stim_time=150*ms, N=1000,
         # Build stimulation
         stim = br2.SpikeGeneratorGroup(1, [0], [stim_time - dt])
         stim_syn = br2.Synapses(stim, G, on_pre="V = 2*Theta")
-        stim_syn.connect(i=0, j=np.arange(GROUP_SIZE))
+        stim_syn.connect(i=0, j=np.arange(group_size))
 
     # Build recurrent synaptic connections
     connections = np.random.rand(N, N) < 0.3
@@ -146,7 +144,7 @@ def run(runtime=250*ms, stim_time=150*ms, N=1000,
     inh_syn.connect(i=inh_i, j=inh_j)
     inh_syn.w = w_in
 
-    # Set random initial conditions
+    # Set random initial conditiong
     G.V = np.random.rand(N) * Theta
 
     if store_spikes:
@@ -176,7 +174,7 @@ run_with_cache = mem.cache(run)
 
 
 def run_and_bin(ext, inh, linear, repetition, stim_time=150*ms, dt=0.1*ms,
-                seed=None):
+                seed=None, group_size=100):
     """Run the network and bin the resulting spike rates with the `bin_spikes`
     function. Return the extracted information needed to classify runs into the
     four categories (see `classify_run`). This information is returned as a
@@ -190,7 +188,7 @@ def run_and_bin(ext, inh, linear, repetition, stim_time=150*ms, dt=0.1*ms,
     # Run simulation
[…]

### 2018-03-06 code/main.py

@@ -9,8 +9,6 @@ from brian2 import mV, us, ms
 from joblib import Parallel, delayed
 import matplotlib.pyplot as plt
 
-# Adding the line below to modify GROUP_SIZE
-import lib
 from lib import run_with_cache, group_size_evolutions, calc_group_evolution_cached, decide_color, grid_search
 from plot import plot_population_activity, plot_markov, plot_grid
 
@@ -28,6 +26,7 @@ if not os.path.exists(FIG_FOLDER):
 
 # Set figure options from configuration file
 plt.style.use('figures.conf')
+
 
 def generate_seeds(main_seed, n_seeds):
     np.random.seed(main_seed)
@@ -59,11 +58,11 @@ def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
     if not quiet:
         print('Running simulations for Figure 3 ({} '
               'coupling) with group_size {}'.format('linear' if linear else 'nonlinear',
-                                              group_size))
+                                                    group_size))
 
     if short:
         par_range = np.linspace(0.16, 0.4, 10, endpoint=True)*mV
-        repetitions = 1
+        repetitions = 5
         name = "grid_short"
     else:
         par_range = np.linspace(0.16, 0.4, 100, endpoint=True)*mV
@@ -72,10 +71,8 @@ def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
 
     seeds = generate_seeds(seed, len(par_range)**2*repetitions)
 
-    # Generate the data
-    lib.GROUP_SIZE = group_size
     grid_results = grid_search(par_range, linear=linear, n_rep=repetitions,
-                               dt=dt, seeds=seeds)
+                               dt=dt, seeds=seeds, group_size=group_size)
     # Plot
     for method, method_string in zip(['max', 'mean'], ['', '_mean']):
         if linear:
@@ -124,9 +121,9 @@ def fig4(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None):
                                                               store_v=True,
                                                               repetition=i,
                                                               seed=seeds[seed_start+i])
-                                     for i in range(1, n_rep))
+                                      for i in range(1, n_rep))
     bins = result_list[0]['bins']
-    v_hist = np.sum(np.array([r['v'] for r in result_list],dtype=float), axis=0)
+    v_hist = np.sum(np.array([r['v'] for r in result_list], dtype=float), axis=0)
[…]

### 2018-03-06 code/main.py
Slightly change the format of the grid filenames

@@ -57,8 +57,9 @@ def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
     (https://doi.org/10.1371/journal.pcbi.1002384.g003)"""
     if not quiet:
         print('Running simulations for Figure 3 ({} '
-              'coupling) with group_size {}'.format('linear' if linear else 'nonlinear',
-                                                    group_size))
+              'coupling) with initial '
+              'group size {}'.format('linear' if linear else 'nonlinear',
+                                     group_size))
 
     if short:
         par_range = np.linspace(0.16, 0.4, 10, endpoint=True)*mV
@@ -76,10 +77,11 @@ def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
     # Plot
     for method, method_string in zip(['max', 'mean'], ['', '_mean']):
         if linear:
-            figname = name + "_l_dt_%.0fus%s.pdf" % (dt/us, method_string)
+            figname = name + "_l_dt_%.0fus_gs%d%s.pdf" % (dt/us, group_size,
+                                                          method_string)
         else:
-            figname = name + "_nl_dt_%.0fus%s_gs%s.pdf" % (dt/us, method_string,
-                                                           group_size)
+            figname = name + "_nl_dt_%.0fus_gs%d%s.pdf" % (dt/us, group_size,
+                                                           method_string)
         colors = np.zeros((len(par_range), len(par_range), 3))
         for i, j in product(range(len(par_range)), range(len(par_range))):
             c = decide_color(grid_results[par_range[i]/mV, par_range[j]/mV],

### 2018-03-06 code/lib.py
Add random spikes initially "in transit"

@@ -88,7 +88,7 @@ def run(runtime=250*ms, stim_time=150*ms, N=1000,
     V0 = 17.6 * mV / tau_m
 
     if linear:
-        # Build the group of neuron to use
+        # Build the group of neurons to use
         eq = "dV/dt = -gamma*V + V0 : volt"
         G = br2.NeuronGroup(N, model=eq, threshold="V>Theta",
                             reset="V=0*mV", method='euler')
@@ -105,6 +105,36 @@ def run(runtime=250*ms, stim_time=150*ms, N=1000,
         stim_syn = br2.Synapses(stim, G, on_pre="V = 2*Theta")
         stim_syn.connect(i=0, j=np.arange(group_size))
 
+    # Number of spikes initially "in transit" (between 1 and 50 (inclusive))
+    n_transit_spikes = np.random.random_integers(50)
+    # "In transit" means that the spikes arrive in the first 5ms, i.e. as if
+    # triggered by events before the start of the simulation (the synaptic delay
+    # is 5ms and therefore all spikes triggered by neurons within the network
+    # will arrive later than that).
+    transit_spikes = br2.SpikeGeneratorGroup(n_transit_spikes,
+                                             np.arange(n_transit_spikes),
+                                             np.random.rand(n_transit_spikes)*5*ms)
+
+    # We'll assume the initial spikes are 50% excitatory and 50% inhibitory
+    n_inh_transit_spikes = n_transit_spikes//2
+    n_exc_transit_spikes = n_transit_spikes - n_inh_transit_spikes
+    if n_inh_transit_spikes > 0:
+        inh_transit_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
+                                       on_pre='V -= w', delay=5 * ms - dt)
+        inh_transit_syn.connect(i=np.arange(n_inh_transit_spikes),
+                                j=np.random.randint(N, size=n_inh_transit_spikes))
+        inh_transit_syn.w = w_in
+
+    if linear:  # See explanations about linear vs. non-linear coupling below
+        exc_transit_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
+                                       on_pre='V += w', delay=5 * ms - dt)
+    else:
+        exc_transit_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
+                               on_pre='ve += w', delay=5 * ms - dt)
[…]

### 2018-03-07 code/plot.py
Update plotting code for Fig. 3 of original paper (plot 3 panels instead of 2)

@@ -61,16 +61,17 @@ def plot_population_activity(results, ymax1=250, save=None, dt=0.1*ms):
 
 def plot_grid(par_range, colors, save=None):
     """Draw the result of a parameter search"""
-    fig, ax = plt.subplots(gridspec_kw={'top': 0.95,
+    fig, ax = plt.subplots(figsize=(1.72, 1.72),  # three panels
+                           gridspec_kw={'top': 0.95,
                                         'right': 0.95,
-                                        'left': 0.175,
-                                        'bottom': 0.15})
+                                        'left': 0.25,
+                                        'bottom': 0.23})
     ax.imshow(colors, extent=[min(par_range/mV),
                               max(par_range/mV),
                               max(par_range/mV),
                               min(par_range/mV)])
-    ax.set_xlabel("Total ext weight")
-    ax.set_ylabel("Total Inh weight")
+    ax.set(xlabel="Total excitatory weight", ylabel="Total inhibitory weight",
+           xticks=[30, 45, 60], yticks=[30, 45, 60])
     save_fig(save, fig=fig)
 
 

### 2018-03-07 code/main.py
Cosmetic figure changes

@@ -87,7 +87,10 @@ def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
             c = decide_color(grid_results[par_range[i]/mV, par_range[j]/mV],
                              method=method)
             colors[j][i] = np.array(c)
-        plot_grid(par_range * 150, colors, save=FIG_FOLDER + figname)
+        # We only add the ylabel to the left-most panel
+        show_ylabel = linear and group_size == 100
+        plot_grid(par_range * 150, colors, show_ylabel=show_ylabel,
+                  save=FIG_FOLDER + figname)
 
 
 def fig4(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None):
@@ -106,8 +109,8 @@ def fig4(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None):
         n_rep = 50
         step_size = 1
 
-    gsize_x = np.arange(1, 180, 5)
-    analytic_x = np.arange(1, 180, step_size)
+    gsize_x = np.arange(1, 182, 5)
+    analytic_x = np.arange(1, 182, step_size)
     seeds = generate_seeds(seed, len(gsize_x)*n_rep + n_rep)
     # Numerical results
     gsize = Parallel(n_jobs=-2)(delayed(group_size_evolutions)(i, n_rep,

### 2018-03-07 code/plot.py

@@ -29,15 +29,16 @@ def plot_population_activity(results, ymax1=250, save=None, dt=0.1*ms):
     plt.figure()
     # Draw the raster plot
     ax_raster.vlines(np.arange(150, 250, 5), 0, 200, color="gray", linestyle='dashed')
-    ax_raster.plot(spikes_t/ms, spikes_i, '|', color="black")
+    ax_raster.plot(spikes_t/ms, spikes_i + 1, '|', color="black")  # Plot a 1-based neuron index
     red_spikes = ((spikes_t >= 150*ms) &
                   ((spikes_t % (5*ms) < dt / 2) |
                    (spikes_t % (5*ms) > (5*ms - dt / 2))))
 
-    ax_raster.plot(spikes_t[red_spikes]/ms, spikes_i[red_spikes], 'r|')
+    ax_raster.plot(spikes_t[red_spikes]/ms, spikes_i[red_spikes] + 1, 'r|')
 
     ax_raster.set(xlim=(110, 220), ylim=(0, 200), xlabel='Time (ms)',
-                  ylabel='Neuron')
+                  ylabel='Neuron', xticks=[120, 150, 180, 210],
+                  yticks=[1, 100, 200])
 
     bins = np.arange(0, 250 + dt/ms, dt/ms)
     binned_activity, _ = np.histogram(spikes_t / ms, bins)
@@ -50,16 +51,16 @@ def plot_population_activity(results, ymax1=250, save=None, dt=0.1*ms):
 
     # Draw the population rate
     ax_binned.bar(bins[:-1], binned_activity, color="black")
-    ax_binned.set(ylim=(0, ymax1), ylabel='Rate')
+    ax_binned.set(ylim=(0, ymax1), ylabel='Rate', yticks=[0, 100, 200])
 
     # Draw the group size
     ax_groups.bar(np.arange(150, 250, 5), group_size, color='red')
-    ax_groups.set(ylim=(0, ymax1), ylabel="g'")
+    ax_groups.set(ylim=(0, ymax1), ylabel="g'", yticks=[0, 100, 200])
 
     save_fig(save, fig)
 
 
-def plot_grid(par_range, colors, save=None):
+def plot_grid(par_range, colors, show_ylabel=True, save=None):
     """Draw the result of a parameter search"""
     fig, ax = plt.subplots(figsize=(1.72, 1.72),  # three panels
                            gridspec_kw={'top': 0.95,
@@ -70,8 +71,10 @@ def plot_grid(par_range, colors, save=None):
[…]

### 2018-03-07 article/Caze_2018.tex
Update figures in article

@@
 \centering
-\begin{subfigure}[t]{0.5\textwidth}
+\begin{subfigure}[t]{0.33\textwidth}
 \caption{}\vspace{-1ex}
-\includegraphics[width=\textwidth]{Figs/grid_l_dt_100us_mean.pdf}
+\includegraphics[width=\textwidth]{Figs/grid_l_dt_100us_gs100_mean.pdf}
 \end{subfigure}%
-\begin{subfigure}[t]{0.5\textwidth}
+\begin{subfigure}[t]{0.33\textwidth}
 \caption{}\vspace{-1ex}
-\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_mean.pdf}
+\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_gs100_mean.pdf}
+\end{subfigure}
+\begin{subfigure}[t]{0.33\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_gs75_mean.pdf}
 \end{subfigure}
 \caption{\label{fig:grid}
-\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for linearly (A) and non-linearly (B) coupled networks.} For each combination, we initiated synchronous activity with 100 neurons and assessed the stability of the temporal evolution.
+\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for linearly (A) and non-linearly (B, C) coupled networks.} For each combination, we initiated synchronous activity with 100 (A, B) or 75 (C) neurons and assessed the stability of the temporal evolution.
 Blue colouring indicates stable propagation of synchrony, red indicates unstable background activity before onset of propagation, yellow indicates unstable background activity after onset of propagation, and green colouring indicates the absence of propagation (see Methods for details).\\

### 2018-03-08 code/plot.py
Fix incorrectly plotted rate histogram (plotted for 0.1ms instead of 1ms)

@@ -40,6 +40,10 @@ def plot_population_activity(results, ymax1=250, save=None, dt=0.1*ms):
                   ylabel='Neuron', xticks=[120, 150, 180, 210],
                   yticks=[1, 100, 200])
 
+    # Note that we use the simulation dt as the bin size here, so that we don't
+    # lose any time resolution when checking for spikes triggered by the
+    # synchronous stimulation. When plotting the population rate, we however
+    # bin into bins of 1ms
     bins = np.arange(0, 250 + dt/ms, dt/ms)
     binned_activity, _ = np.histogram(spikes_t / ms, bins)
     # Select the spikes that (most likely) arise from the synchronous
@@ -49,8 +53,11 @@ def plot_population_activity(results, ymax1=250, save=None, dt=0.1*ms):
     delay_steps = int(round(5*ms/dt))
     group_size = binned_activity[int(round(150*ms/dt))::delay_steps]
 
-    # Draw the population rate
-    ax_binned.bar(bins[:-1], binned_activity, color="black")
+    # Draw the population rate (with 1ms bins)
+    steps_per_bin = int(round(1*ms/dt))
+    binned_activity_1ms = binned_activity.reshape(-1, steps_per_bin).sum(axis=1)
+    ax_binned.bar(bins[:-1:steps_per_bin], binned_activity_1ms,
+                  color="black")
     ax_binned.set(ylim=(0, ymax1), ylabel='Rate', yticks=[0, 100, 200])
 
     # Draw the group size

### 2018-03-08 article/Caze_2018.tex
Update Caze_2018.tex
Need to compile the tex file I changed the thing in four locations (as we saw). Also need to update the rebuttal.doc to refer to the changes (line ref in tex)

@@
 
+Our replication present slight differences with the original grid search.
+The stable region surface ends up earlier in a regime with strong inhibitory connections.
+The odd blue-yellow-red region presents in the original article differs from the continuous transition we obtained in our simulations.
+Implementation details might explain these differences
+
 To numerically derive the evolution of synchronous pulse sizes presented in Fig.~\ref{fig:markov} (for the semi-analytical approach, see the next section), we performed simulations of \SI{56}{\milli\second} each.
@@
 We did not attempt to replicate the analytical solution for the evolution of synchronous pulses based on diffusion approximation (blue dots in Fig.~4 of \cite{Memmesheimer2012}).
+The article explains in more details the semi-analytical work that was more straightforward to reproduce.
 To calculate the semi-analytical solutions for Fig.~\ref{fig:markov}, based on a numerical estimate of the distribution $P(V)$, we proceeded as follows.
@@
 
+The result of our simulation seems shifted upward compared to the original work.
+This difference is most visible at the origin of the plot.
+This might come from "false positive" spikes generated by the background activity (~5 spikes more in our simulation results).
+Yet our work strengthen the original result demonstrating a qualitative difference between linearly coupled and non-linearly coupled networks.
+
 \section*{Discussion}
@@
 We managed to qualitatively reproduce the main results of Raoul-Martin Memmes\-heimer and Marc Timme \cite{Memmesheimer2012} despite some slight quantitative differences.
+The grid search differs in certain regions and the markov analysis demonstrate a slight shifth upward for the numerical results.
 These difference could be due to our use of clock-based instead of event-driven simulations, as it forces all activity to a temporal grid of finite precision.

### 2018-03-08 code/lib.py
Run a small part of the grid search for various dts Needs cleaning up in main.py and better plotting

@@ -13,7 +13,7 @@ mem = Memory(cachedir='./__joblib_cache__', verbose=0, compress=True)
 
 
 def group_size_evolutions(group_size, n_rep=1, linear=True, dt=0.1*ms,
-                          seeds=None):
+                          bias_correction=False, seeds=None):
     """Return the evolution of the group size after one cycle"""
     group_ev = []
     for rep in range(n_rep):
@@ -24,7 +24,14 @@ def group_size_evolutions(group_size, n_rep=1, linear=True, dt=0.1*ms,
         results = run_with_cache(56 * ms, group_size=group_size,
                                  stim_time=50 * ms, linear=linear,
                                  repetition=rep, dt=dt, seed=seed)
-        group_ev.append(np.sum(np.abs(results['t'] - 55 * ms) < dt / 2))
+        next_iteration = np.sum(np.abs(results['t'] - 55 * ms) < dt / 2)
+        if bias_correction:
+            spikes_before_stim = np.sum(results['t'] < 50*ms)
+            # Reduce the group size by the number of spikes that we'd expect
+            # by chance in a time step with the given background activity.
+            correction = spikes_before_stim / (50*ms/dt)
+            next_iteration -= correction
+        group_ev.append(next_iteration)
     return group_ev
 
 
@@ -252,22 +259,28 @@ def do_repetitions(ext, inh, linear, n_rep, dt=0.1*ms, seeds=None,
 
 
 @mem.cache
-def grid_search(weights=np.arange(0.16, 0.4, 0.375/150.)*mV,
+def grid_search(weights_exc=np.arange(0.16, 0.4, 0.375/150.)*mV,
+                weights_inh=None,
                 n_rep=1, linear=True, quiet=False, dt=0.1*ms, seeds=None,
                 group_size=100):
     """Perform a grid search over the given parameter range for excitatory and
-    inhibitory synaptic connection strengths. Returns a dictionary mapping each
-    combination of excitatory and inhibitory weights (provided as a tuple
-    ``(exc, inh)`` to a list of results (as returned by `run_and_bin`)."""
+    inhibitory synaptic connection strengths. If only the parameter range for
+    excitatory connections is specified, then the same range is used for
+    inhibitory connections.
+    Returns a dictionary mapping each combination of excitatory and inhibitory
+    weights (provided as a tuple ``(exc, inh)`` to a list of results (as
+    returned by `run_and_bin`)."""
+    if weights_inh is None:
+        weights_inh = weights_exc
     results = {}
[…]

### 2018-03-08 code/main.py

@@ -19,7 +19,8 @@ br2.prefs.codegen.target = 'cython'
 
 FIG_FOLDER = "../article/Figs/"
 
-main_seeds = [3982293089, 1861487226, 2570878100, 3472600360, 2780156760]
+main_seeds = [3982293089, 1861487226, 2570878100, 3472600360, 2780156760,
+              1966509933, 1687607157]
 
 if not os.path.exists(FIG_FOLDER):
     os.makedirs(FIG_FOLDER)
@@ -50,6 +51,7 @@ def fig2(quiet=False, dt=0.1*ms, seed=None):
     plot_population_activity(results_nl, save=FIG_FOLDER + figname, dt=dt)
 
 
+ 
 def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
          group_size=100):
     """Perform a grid search over the excitatory and inhibitory coupling
@@ -87,19 +89,64 @@ def fig3(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
             c = decide_color(grid_results[par_range[i]/mV, par_range[j]/mV],
                              method=method)
             colors[j][i] = np.array(c)
+    
         # We only add the ylabel to the left-most panel
         show_ylabel = linear and group_size == 100
-        plot_grid(par_range * 150, colors, show_ylabel=show_ylabel,
+        plot_grid(par_range * 150, par_range * 150, colors,
+                  show_ylabel=show_ylabel, save=FIG_FOLDER + figname)
+
+def fig3_detail(linear=True, short=True, quiet=False, dt=0.1*ms, seed=None,
+         group_size=100):
+    if not quiet:
+        print('Running simulations for detail of Figure 3 ({} '
+              'coupling) with initial '
+              'group size {}'.format('linear' if linear else 'nonlinear',
+                                     group_size))
+
+    if short:
+        par_range = np.linspace(0.16, 0.4, 10, endpoint=True)*mV
+        par_range_inh = par_range[0:3]
+        par_range_exc = par_range[3:6]
+        repetitions = 5
+        name = "grid_short"
+    else:
+        par_range = np.linspace(0.16, 0.4, 100, endpoint=True)*mV
+        par_range_inh = par_range[0:30]
+        par_range_exc = par_range[30:60]
+        repetitions = 10
+        name = "grid"
+
+    seeds = generate_seeds(seed, len(par_range_inh)*len(par_range_exc)*repetitions)
+
[…]

### 2018-03-08 code/plot.py

@@ -67,17 +67,17 @@ def plot_population_activity(results, ymax1=250, save=None, dt=0.1*ms):
     save_fig(save, fig)
 
 
-def plot_grid(par_range, colors, show_ylabel=True, save=None):
+def plot_grid(par_range_exc, par_range_inh, colors, show_ylabel=True, save=None):
     """Draw the result of a parameter search"""
     fig, ax = plt.subplots(figsize=(1.72, 1.72),  # three panels
                            gridspec_kw={'top': 0.95,
                                         'right': 0.95,
                                         'left': 0.25,
                                         'bottom': 0.23})
-    ax.imshow(colors, extent=[min(par_range/mV),
-                              max(par_range/mV),
-                              max(par_range/mV),
-                              min(par_range/mV)])
+    ax.imshow(colors, extent=[min(par_range_exc/mV),
+                              max(par_range_exc/mV),
+                              max(par_range_inh/mV),
+                              min(par_range_inh/mV)])
     ax.set(xlabel="Total excitatory weight",
            xticks=[30, 45, 60], yticks=[30, 45, 60])
     if show_ylabel:

### 2018-03-08 code/lib.py
Add comments about the usage of mem.cache

@@ -69,8 +69,11 @@ def calc_group_evolution(bins, v_hist, group_size, w_ex=0.2*mV, w_in=0.2*mV,
             P_spike += P_triggered * P_conn(group_size, n_ex, n_in, p_0, p_ex, p_in)
     return (N - group_size)*P_spike
 
+# Note that this is the same as adding the @mem.cache decorator to the function,
+# but the decorator leaves the name of the function unchanged which leads to
+# problems with joblib's Parallel/delayed mechanism
+# (see https://github.com/joblib/joblib/issues/226)
 calc_group_evolution_cached = mem.cache(calc_group_evolution)
-
 
 def run(runtime=250*ms, stim_time=150*ms, N=1000,
         linear=True, w_ex=0.2*mV, w_in=0.2*mV, repetition=0,
@@ -203,6 +206,7 @@ def run(runtime=250*ms, stim_time=150*ms, N=1000,
         results['v'], results['bins'] = np.histogram(v_mon.V/mV, bins=bins)
     return results
 
+# (See note for calc_group_evolution_cached above)
 run_with_cache = mem.cache(run)
 
 
@@ -237,9 +241,7 @@ def run_and_bin(ext, inh, linear, repetition, stim_time=150*ms, dt=0.1*ms,
               np.max(after_stim))
     return result
 
-# Note that this is the same as adding the decorator @mem.cached to the function
-# above, but this form of usage (where the function name is unchanged) is not
-# compatible with the multipprocessing approach we use in `do_repetions`.
+# (See note for calc_group_evolution_cached above)
 run_and_bin_cached = mem.cache(run_and_bin)
 
 

### 2018-03-09 REBUTTAL.md
Moving rebuttal and last version of tex

We want to thank the reviewers for their well-intentioned and valuable
comments. We describe here how we change the manuscript to adress their
comments.

> There's a small typo in the code README, last section on parallelization
> reads 'multiple CPU cores a moder computer provide'.

We corrected the typo.

> In Figure 2 (of the replication), I appreciate the switch from the
> epsilon+subscript axis labels used in the paper to plain text, which
> avoids having to read the caption. In line with that, I think using full text
> for inhibitory and excitatory (instead of Inh and ext) would be even clearer.

We modified the axis name to have full text inhibitory et excitatory

> Apologies if I missed it, but I don't understand why the replication of Figure 3c is
skipped. I understand that the crux of the matter is captured by a and b, but
was there a particular reason why it was omitted (e.g. computation time)?  We
added the third panel.  I would encourage, in the concluding Discussion
section, a brief recap of the differences found (detail in Figure 2,
underestimation in Figure 3) before discussing the potential causes.  We
modified the discussion accordingly I haven't gone through the details of the
derivation of the semi-analytic solution yet, but I think it would be useful to
have a sentence or two specifying if/where the derivation presented differs
from the original one.  The difference lays in how we sample the voltage
distribution otherwise we did a similar computation I don't fully agree with
the the statement that the semi-analytical result underestimates the numerical
one, if anything to me it looks shifted to the right (underestimates before the
peak, overestimates after).  We corrected the text, the difference stem wgqwweee
think from the estimation of voltage distribution.  I am slightly confused by
how you obtain a numerical approximation of P(V) as opposed to how the original
paper does it. From what I understand, you build 50 linear networks and 50
nonlinear networks (with random connectivity )and simulate each network once
for 250ms (but from how it's written it could sound as though you are running
multiple simulations of the same two networks - i.e. with the same
connections), whereas in the original they build 100 random networks (50 and
50) and simulate each ten times. Could you clarify what simulations you are
running to estimate P(V) and how they compare to what the original paper does?
It may also be good to address this difference in the paper, as you have done
in most other cases.  We clarified this point in the main text Edit: I think my
confusion in the point above may also be partly due to the fact that when you
say 'a network is simulated n times' you mean that also new random connectivity
is generated in each simulation (whereas for me intuitively simulating a
network n times means keeping the architecture and drawing new initial
potentials). This becomes clear since elsewhere you say: 'Each network was
simulated 10 times with different initial conditions (synaptic connections and
initial membrane potential values)'. It may be good to be explicit for clarity
We now further clarify this point.  Major issue: First, while many of the
decisions made by the authors have been explained, such as the choice of Brian
and certain parameter adjustments, I am missing an explanation for why the
authors decided not to use the original analytical solution as well.
Furthermore, differences between this Figure (3) and the original that are
described are too short. Instead of only replicating the figure and describing
a "good match", I would like to see a more quantitative comparison (e.g.,
position of the maximum, intersections, etc.). The same applies to Fig. 2 (see
below).  Minor issues: Manuscript: Nice introduction. In line 2, there should
be a comma after "However". Maybe, a final sentence could summarize the main
findings of the replication.  Methods are very intuitive and sufficiently
described. On page 1, I would suggest removing "dynamic" after membrane
potential. Also, in my personal opinion, often used comments in brackets
disturb the flow of reading.  In Eq. 1, I would reformat the brackets encasing
the nonlinear function to be larger.  On page 2, there is a period mark missing
when describing the spike train function \epsilon.  Why is the equation for the
nonlinearity function not numbered? I would also suggest moving the commas
after the cases. After "otherwise" there should be a period mark.  When
describing the biological observation of nonlinearity only affecting
synchronous spikes, I would like to see references.  Fantastic description of
what the neuron model effectively is (point neuron with a single nonlinear
dendrite) I enjoyed reading the argumentation for a clock-driven model with
finite precision in terms of biological plausibility.  The description for
implementing the nonlinear networks could be rewritten to match closer the
mathematical definitions. Start with describing the use of the clipping
function to achieve the nonlinearity function, then explain that ve is used as
a placeholder variable equivalent to x from the equation.  Nice description and
use of the joblib package.  In describing the grid search, I would write: "For
the grid search presented in Fig. 2, we varied inhibitory and excitatory
synaptic weights between 0.16 mV and 0.4 mV. Given that each neuron receives on
average 150 excitatory and 150 inhibitory inputs, this corresponds to an
average total weight between [...]" Below on page 4, there is a space missing
for "50 ms".  The derivation of the semi-analytical approach is well derived
and described sufficiently.  I would add to the Eq. 6 description, that it is
the expected value of spiking neurons in the next iteration given a certain
initial synchronous pulse (g_i^').  Results section describes the similarities
between original and replication sufficiently, but mainly in qualitative terms.
In Fig. 1, I would suggest using similar yticks for the rate and the number of
synchronous spikes, as well as the xticks for the time. This allows a much
better quantitative evaluation of the reproducibility of the original study.
In Fig. 2, the description of the resulting color code is very elucidating, as
this was not very well explained in the original study.  I would like to
suggest to explain, why the C panel from the original study has not been
replicated and further the differences could be described in more detail. I
also see differences for large weights (both exc. and inh.), as well as
qualitative differences for the linear network (no yellow line/areas). In B,
the area of unstable activity before stimulation seems to be significantly
larger.  Why did the authors not try the initial random spikes in transit?
Fig. 3 I discussed in the major point above.  Code: Well written, a bit
under-commented, but clearly structured The easy installation of requirements
and use of CL options make the code very reusable and in general user-friendly
In lib.py, I am a bit puzzled about the way how the function "run_with_cache"
is defined. Why can't the run function be decorated with @mem.cache as for the
other functions?  Could the authors elaborate on the definition of V0 in line
81. It does not seem to be included in Table 1 or the main text.  On first run,
I got thrown a ton of FutureWarnings concerning the use of certain dtypes in
Brian. I think this is related to the version/system I was using (although I
used the requirements.txt to get the exact version numbers). I omitted the
warnings by using the Warnings library to ignore any FutureWarnings I then
performed the simulations using the --long option, which finished after 7h38m.

### 2018-03-09 REBUTTAL.md
Addressing RW1 comments

@@
 
+=== RW1 ===
+
 > There's a small typo in the code README, last section on parallelization
@@
 
-We corrected the typo.
+We corrected the typo in the README file.
 
 > In Figure 2 (of the replication), I appreciate the switch from the
-> epsilon+subscript axis labels used in the paper to plain text, which
-> avoids having to read the caption. In line with that, I think using full text
-> for inhibitory and excitatory (instead of Inh and ext) would be even clearer.
+> epsilon+subscript axis labels used in the paper to plain text, which avoids
+> having to read the caption. In line with that, I think using full text for
+> inhibitory and excitatory (instead of Inh and ext) would be even clearer.
 
@@
 
-> Apologies if I missed it, but I don't understand why the replication of Figure 3c is
-skipped. I understand that the crux of the matter is captured by a and b, but
-was there a particular reason why it was omitted (e.g. computation time)?  We
-added the third panel.  I would encourage, in the concluding Discussion
-section, a brief recap of the differences found (detail in Figure 2,
-underestimation in Figure 3) before discussing the potential causes.  We
-modified the discussion accordingly I haven't gone through the details of the
-derivation of the semi-analytic solution yet, but I think it would be useful to
-have a sentence or two specifying if/where the derivation presented differs
-from the original one.  The difference lays in how we sample the voltage
-distribution otherwise we did a similar computation I don't fully agree with
-the the statement that the semi-analytical result underestimates the numerical
-one, if anything to me it looks shifted to the right (underestimates before the
-peak, overestimates after).  We corrected the text, the difference stem wgqwweee
-think from the estimation of voltage distribution.  I am slightly confused by
-how you obtain a numerical approximation of P(V) as opposed to how the original
-paper does it. From what I understand, you build 50 linear networks and 50
-nonlinear networks (with random connectivity )and simulate each network once
-for 250ms (but from how it's written it could sound as though you are running
-multiple simulations of the same two networks - i.e. with the same
-connections), whereas in the original they build 100 random networks (50 and
-50) and simulate each ten times. Could you clarify what simulations you are
-running to estimate P(V) and how they compare to what the original paper does?
-It may also be good to address this difference in the paper, as you have done
-in most other cases.  We clarified this point in the main text Edit: I think my
-confusion in the point above may also be partly due to the fact that when you
-say 'a network is simulated n times' you mean that also new random connectivity
-is generated in each simulation (whereas for me intuitively simulating a
-network n times means keeping the architecture and drawing new initial
-potentials). This becomes clear since elsewhere you say: 'Each network was
-simulated 10 times with different initial conditions (synaptic connections and
-initial membrane potential values)'. It may be good to be explicit for clarity
-We now further clarify this point.  Major issue: First, while many of the
-decisions made by the authors have been explained, such as the choice of Brian
-and certain parameter adjustments, I am missing an explanation for why the
-authors decided not to use the original analytical solution as well.
-Furthermore, differences between this Figure (3) and the original that are
-described are too short. Instead of only replicating the figure and describing
-a "good match", I would like to see a more quantitative comparison (e.g.,
-position of the maximum, intersections, etc.). The same applies to Fig. 2 (see
-below).  Minor issues: Manuscript: Nice introduction. In line 2, there should
-be a comma after "However". Maybe, a final sentence could summarize the main
-findings of the replication.  Methods are very intuitive and sufficiently
-described. On page 1, I would suggest removing "dynamic" after membrane
-potential. Also, in my personal opinion, often used comments in brackets
-disturb the flow of reading.  In Eq. 1, I would reformat the brackets encasing
-the nonlinear function to be larger.  On page 2, there is a period mark missing
-when describing the spike train function \epsilon.  Why is the equation for the
-nonlinearity function not numbered? I would also suggest moving the commas
-after the cases. After "otherwise" there should be a period mark.  When
-describing the biological observation of nonlinearity only affecting
-synchronous spikes, I would like to see references.  Fantastic description of
-what the neuron model effectively is (point neuron with a single nonlinear
-dendrite) I enjoyed reading the argumentation for a clock-driven model with
-finite precision in terms of biological plausibility.  The description for
-implementing the nonlinear networks could be rewritten to match closer the
-mathematical definitions. Start with describing the use of the clipping
-function to achieve the nonlinearity function, then explain that ve is used as
-a placeholder variable equivalent to x from the equation.  Nice description and
-use of the joblib package.  In describing the grid search, I would write: "For
-the grid search presented in Fig. 2, we varied inhibitory and excitatory
-synaptic weights between 0.16 mV and 0.4 mV. Given that each neuron receives on
-average 150 excitatory and 150 inhibitory inputs, this corresponds to an
-average total weight between [...]" Below on page 4, there is a space missing
-for "50 ms".  The derivation of the semi-analytical approach is well derived
-and described sufficiently.  I would add to the Eq. 6 description, that it is
-the expected value of spiking neurons in the next iteration given a certain
-initial synchronous pulse (g_i^').  Results section describes the similarities
-between original and replication sufficiently, but mainly in qualitative terms.
-In Fig. 1, I would suggest using similar yticks for the rate and the number of
-synchronous spikes, as well as the xticks for the time. This allows a much
-better quantitative evaluation of the reproducibility of the original study.
-In Fig. 2, the description of the resulting color code is very elucidating, as
-this was not very well explained in the original study.  I would like to
-suggest to explain, why the C panel from the original study has not been
-replicated and further the differences could be described in more detail. I
-also see differences for large weights (both exc. and inh.), as well as
-qualitative differences for the linear network (no yellow line/areas). In B,
-the area of unstable activity before stimulation seems to be significantly
-larger.  Why did the authors not try the initial random spikes in transit?
-Fig. 3 I discussed in the major point above.  Code: Well written, a bit
-under-commented, but clearly structured The easy installation of requirements
-and use of CL options make the code very reusable and in general user-friendly
-In lib.py, I am a bit puzzled about the way how the function "run_with_cache"
-is defined. Why can't the run function be decorated with @mem.cache as for the
-other functions?  Could the authors elaborate on the definition of V0 in line
-81. It does not seem to be included in Table 1 or the main text.  On first run,
-I got thrown a ton of FutureWarnings concerning the use of certain dtypes in
-Brian. I think this is related to the version/system I was using (although I
-used the requirements.txt to get the exact version numbers). I omitted the
-warnings by using the Warnings library to ignore any FutureWarnings I then
-performed the simulations using the --long option, which finished after 7h38m.
+> Apologies if I missed it, but I don't understand why the replication of
+> Figure 3c is skipped. I understand that the crux of the matter is captured by
+> a and b, but was there a particular reason why it was omitted (e.g.
+> computation time)?  We added the third panel.
+
+We added the third panel
+
+> I would encourage, in the concluding Discussion section, a brief recap of the
+> differences found (detail in Figure 2, underestimation in Figure 3) before
+> discussing the potential causes.
+
+We modified the discussion accordingly (see L434 in the .tex file)
+
+> I haven't gone through the details of the derivation of the semi-analytic
+> solution yet, but I think it would be useful to have a sentence or two
+> specifying if/where the derivation presented differs from the original one.
+> I don't fully agree with the the statement that the semi-analytical result
+> underestimates the numerical one, if anything to me it looks shifted to the
+> right (underestimates before the peak, overestimates after).  We corrected
+> the text, the difference stem wgqwweee think from the estimation of voltage
+> distribution.  I am slightly confused by how you obtain a numerical
+> approximation of P(V) as opposed to how the original paper does it.
+
+The numerical curve are in fact shifted upwards due to false positve (see
+L430). This is due to false positive spikes.  The difference lays in how we
+sample the voltage distribution otherwise we did a similar computation. We
+acknowledge that details in the original work were unclear to reproduce the
+analytic approach (see L333)
+
+> From what I understand, you build 50 linear networks and 50
+> nonlinear networks (with random connectivity )and simulate each network once
+> for 250ms (but from how it's written it could sound as though you are running
+> multiple simulations of the same two networks - i.e. with the same
+> connections), whereas in the original they build 100 random networks (50 and
+> 50) and simulate each ten times. Could you clarify what simulations you are
+> running to estimate P(V) and how they compare to what the original paper does?
+> It may also be good to address this difference in the paper, as you have done
+> in most other cases.  We clarified this point in the main text Edit: I think my
+> confusion in the point above may also be partly due to the fact that when you
+> say 'a network is simulated n times' you mean that also new random connectivity
+> is generated in each simulation (whereas for me intuitively simulating a
+> network n times means keeping the architecture and drawing new initial
+> potentials). This becomes clear since elsewhere you say: 'Each network was
+> simulated 10 times with different initial conditions (synaptic connections and
+> initial membrane potential values)'. It may be good to be explicit for clarity
+
+We now further clarify this point.
+
+=== RW2 ===
+
+> Major issue: First, while many of the
+> decisions made by the authors have been explained, such as the choice of Brian
+> and certain parameter adjustments, I am missing an explanation for why the
+> authors decided not to use the original analytical solution as well.
+> Furthermore, differences between this Figure (3) and the original that are
+> described are too short. Instead of only replicating the figure and describing
+> a "good match", I would like to see a more quantitative comparison (e.g.,
+> position of the maximum, intersections, etc.). The same applies to Fig. 2 (see
+> below).  Minor issues: Manuscript: Nice introduction. In line 2, there should
+> be a comma after "However". Maybe, a final sentence could summarize the main
+> findings of the replication.  Methods are very intuitive and sufficiently
+> described. On page 1, I would suggest removing "dynamic" after membrane
+> potential. Also, in my personal opinion, often used comments in brackets
+> disturb the flow of reading.  In Eq. 1, I would reformat the brackets encasing
+> the nonlinear function to be larger.  On page 2, there is a period mark missing
+> when describing the spike train function \epsilon.  Why is the equation for the
+> nonlinearity function not numbered? I would also suggest moving the commas
+> after the cases. After "otherwise" there should be a period mark.  When
+> describing the biological observation of nonlinearity only affecting
+> synchronous spikes, I would like to see references.  Fantastic description of
+> what the neuron model effectively is (point neuron with a single nonlinear
+> dendrite) I enjoyed reading the argumentation for a clock-driven model with
+> finite precision in terms of biological plausibility.  The description for
+> implementing the nonlinear networks could be rewritten to match closer the
+> mathematical definitions. Start with describing the use of the clipping
+> function to achieve the nonlinearity function, then explain that ve is used as
+> a placeholder variable equivalent to x from the equation.  Nice description and
+> use of the joblib package.  In describing the grid search, I would write: "For
+> the grid search presented in Fig. 2, we varied inhibitory and excitatory
+> synaptic weights between 0.16 mV and 0.4 mV. Given that each neuron receives on
+> average 150 excitatory and 150 inhibitory inputs, this corresponds to an
+> average total weight between [...]" Below on page 4, there is a space missing
+> for "50 ms".  The derivation of the semi-analytical approach is well derived
+> and described sufficiently.  I would add to the Eq. 6 description, that it is
+> the expected value of spiking neurons in the next iteration given a certain
+> initial synchronous pulse (g_i^').  Results section describes the similarities
+> between original and replication sufficiently, but mainly in qualitative terms.
+> In Fig. 1, I would suggest using similar yticks for the rate and the number of
+> synchronous spikes, as well as the xticks for the time. This allows a much
+> better quantitative evaluation of the reproducibility of the original study.
+> In Fig. 2, the description of the resulting color code is very elucidating, as
+> this was not very well explained in the original study.  I would like to
+> suggest to explain, why the C panel from the original study has not been
+> replicated and further the differences could be described in more detail. I
+> also see differences for large weights (both exc. and inh.), as well as
+> qualitative differences for the linear network (no yellow line/areas). In B,
+> the area of unstable activity before stimulation seems to be significantly
+> larger.  Why did the authors not try the initial random spikes in transit?
+> Fig. 3 I discussed in the major point above.  Code: Well written, a bit
+> under-commented, but clearly structured The easy installation of requirements
+> and use of CL options make the code very reusable and in general user-friendly
+> In lib.py, I am a bit puzzled about the way how the function "run_with_cache"
+> is defined. Why can't the run function be decorated with @mem.cache as for the
+> other functions?  Could the authors elaborate on the definition of V0 in line
+> 81 . It does not seem to be included in Table 1 or the main text.  On first run,
+> I got thrown a ton of FutureWarnings concerning the use of certain dtypes in
+> Brian. I think this is related to the version/system I was using (although I
+> used the requirements.txt to get the exact version numbers). I omitted the
+> warnings by using the Warnings library to ignore any FutureWarnings I then
+> performed the simulations using the --long option, which finished after 7h38m.

### 2018-03-09 REBUTTAL.md
Starting to address RW2 comments when needed

@@
 We want to thank the reviewers for their well-intentioned and valuable
-comments. We describe here how we change the manuscript to adress their
+comments. We describe, when needed, how we change the manuscript to adress their
 comments.
@@
 
-> From what I understand, you build 50 linear networks and 50
-> nonlinear networks (with random connectivity )and simulate each network once
-> for 250ms (but from how it's written it could sound as though you are running
-> multiple simulations of the same two networks - i.e. with the same
-> connections), whereas in the original they build 100 random networks (50 and
-> 50) and simulate each ten times. Could you clarify what simulations you are
-> running to estimate P(V) and how they compare to what the original paper does?
-> It may also be good to address this difference in the paper, as you have done
-> in most other cases.  We clarified this point in the main text Edit: I think my
+> From what I understand, you build 50 linear networks and 50 nonlinear
+> networks (with random connectivity )and simulate each network once for 250ms
+> (but from how it's written it could sound as though you are running multiple
+> simulations of the same two networks - i.e. with the same connections),
+> whereas in the original they build 100 random networks (50 and 50) and
+> simulate each ten times. Could you clarify what simulations you are running
+> to estimate P(V) and how they compare to what the original paper does?  It
+> may also be good to address this difference in the paper, as you have done in
+> most other cases.  We clarified this point in the main text Edit: I think my
 > confusion in the point above may also be partly due to the fact that when you
-> say 'a network is simulated n times' you mean that also new random connectivity
-> is generated in each simulation (whereas for me intuitively simulating a
-> network n times means keeping the architecture and drawing new initial
-> potentials). This becomes clear since elsewhere you say: 'Each network was
-> simulated 10 times with different initial conditions (synaptic connections and
-> initial membrane potential values)'. It may be good to be explicit for clarity
+> say 'a network is simulated n times' you mean that also new random
+> connectivity is generated in each simulation (whereas for me intuitively
+> simulating a network n times means keeping the architecture and drawing new
+> initial potentials). This becomes clear since elsewhere you say: 'Each
+> network was simulated 10 times with different initial conditions (synaptic
+> connections and initial membrane potential values)'. It may be good to be
+> explicit for clarity
 
@@
 
-=== RW2 ===
+# RW2
 
-> Major issue: First, while many of the
-> decisions made by the authors have been explained, such as the choice of Brian
-> and certain parameter adjustments, I am missing an explanation for why the
-> authors decided not to use the original analytical solution as well.
+## Major issue:
+
+> First, while many of the decisions made by the authors have been explained,
+> such as the choice of Brian and certain parameter adjustments, I am missing
+> an explanation for why the authors decided not to use the original analytical
+> solution as well.
+
+We further justify our choice (see L339 in tex file). The analytical was less
+explicitly described than the semi-analytical. We can contact the original
+authors to have further details. We were happy to reproduce at least on the
+approach, but we could try to have it reimplemented when we have further
+details.
+
 > Furthermore, differences between this Figure (3) and the original that are
-> described are too short. Instead of only replicating the figure and describing
-> a "good match", I would like to see a more quantitative comparison (e.g.,
-> position of the maximum, intersections, etc.). The same applies to Fig. 2 (see
-> below).  Minor issues: Manuscript: Nice introduction. In line 2, there should
-> be a comma after "However". Maybe, a final sentence could summarize the main
-> findings of the replication.  Methods are very intuitive and sufficiently
-> described. On page 1, I would suggest removing "dynamic" after membrane
-> potential. Also, in my personal opinion, often used comments in brackets
-> disturb the flow of reading.  In Eq. 1, I would reformat the brackets encasing
-> the nonlinear function to be larger.  On page 2, there is a period mark missing
-> when describing the spike train function \epsilon.  Why is the equation for the
-> nonlinearity function not numbered? I would also suggest moving the commas
-> after the cases. After "otherwise" there should be a period mark.  When
-> describing the biological observation of nonlinearity only affecting
+> described are too short. Instead of only replicating the figure and
+> describing a "good match", I would like to see a more quantitative comparison
+> (e.g., position of the maximum, intersections, etc.). The same applies to
+> Fig. 2 (see below).
+
+## Minor issues
+
+> When describing the biological observation of nonlinearity only affecting
 > synchronous spikes, I would like to see references.  Fantastic description of

### 2018-03-09 REBUTTAL.md
Final addressing of the comments from Romain

@@
 We want to thank the reviewers for their well-intentioned and valuable
-comments. We describe, when needed, how we change the manuscript to adress their
-comments.
+comments. We describe, when needed, how we change the manuscript to adress
+their comments.
 
-=== RW1 ===
+# RW1
 
@@
 > specifying if/where the derivation presented differs from the original one.
+
+The semi analytical work agrees with the original work. It's the numerical
+simulations that differ. (see L430)
+
 > I don't fully agree with the the statement that the semi-analytical result
 > underestimates the numerical one, if anything to me it looks shifted to the
-> right (underestimates before the peak, overestimates after).  We corrected
-> the text, the difference stem wgqwweee think from the estimation of voltage
-> distribution.  I am slightly confused by how you obtain a numerical
-> approximation of P(V) as opposed to how the original paper does it.
+> right (underestimates before the peak, overestimates after).  I am slightly
+> confused by how you obtain a numerical approximation of P(V) as opposed to
+> how the original paper does it.
 
-The numerical curve are in fact shifted upwards due to false positve (see
-L430). This is due to false positive spikes.  The difference lays in how we
-sample the voltage distribution otherwise we did a similar computation. We
+We corrected the text, the difference stems from the numerical simulation
+where the clocking introduce "false positive" spikes absent from a continuous
+model. The numerical curve are in fact shifted upwards due to false positve
+(see L430). This is due to false positive spikes.  The difference lays in how
+we sample the voltage distribution otherwise we did a similar computation. We
 acknowledge that details in the original work were unclear to reproduce the
 analytic approach (see L333)
-
-> From what I understand, you build 50 linear networks and 50 nonlinear
-> networks (with random connectivity )and simulate each network once for 250ms
-> (but from how it's written it could sound as though you are running multiple
-> simulations of the same two networks - i.e. with the same connections),
-> whereas in the original they build 100 random networks (50 and 50) and
-> simulate each ten times. Could you clarify what simulations you are running
-> to estimate P(V) and how they compare to what the original paper does?  It
-> may also be good to address this difference in the paper, as you have done in
-> most other cases.  We clarified this point in the main text Edit: I think my
-> confusion in the point above may also be partly due to the fact that when you
-> say 'a network is simulated n times' you mean that also new random
-> connectivity is generated in each simulation (whereas for me intuitively
-> simulating a network n times means keeping the architecture and drawing new
-> initial potentials). This becomes clear since elsewhere you say: 'Each
-> network was simulated 10 times with different initial conditions (synaptic
-> connections and initial membrane potential values)'. It may be good to be
-> explicit for clarity
-
-We now further clarify this point.
 
@@
 
+We further explicit the differences from the original work (See L328).
+@stimberg should we change the figure.2?
+
 ## Minor issues
 
-> When describing the biological observation of nonlinearity only affecting
-> synchronous spikes, I would like to see references.  Fantastic description of
-> what the neuron model effectively is (point neuron with a single nonlinear
-> dendrite) I enjoyed reading the argumentation for a clock-driven model with
-> finite precision in terms of biological plausibility.  The description for
-> implementing the nonlinear networks could be rewritten to match closer the
+> The description for implementing the nonlinear networks could be rewritten to match closer the
 > mathematical definitions. Start with describing the use of the clipping
 > function to achieve the nonlinearity function, then explain that ve is used as
-> a placeholder variable equivalent to x from the equation.  Nice description and
-> use of the joblib package.  In describing the grid search, I would write: "For
-> the grid search presented in Fig. 2, we varied inhibitory and excitatory
-> synaptic weights between 0.16 mV and 0.4 mV. Given that each neuron receives on
-> average 150 excitatory and 150 inhibitory inputs, this corresponds to an
-> average total weight between [...]" Below on page 4, there is a space missing
-> for "50 ms".  The derivation of the semi-analytical approach is well derived
-> and described sufficiently.  I would add to the Eq. 6 description, that it is
-> the expected value of spiking neurons in the next iteration given a certain
-> initial synchronous pulse (g_i^').  Results section describes the similarities
-> between original and replication sufficiently, but mainly in qualitative terms.
-> In Fig. 1, I would suggest using similar yticks for the rate and the number of
-> synchronous spikes, as well as the xticks for the time. This allows a much
-> better quantitative evaluation of the reproducibility of the original study.
-> In Fig. 2, the description of the resulting color code is very elucidating, as
-> this was not very well explained in the original study.  I would like to
-> suggest to explain, why the C panel from the original study has not been
+> a placeholder variable equivalent to x from the equation.
+
+> The C panel from the original study has not been
 > replicated and further the differences could be described in more detail. I
@@
 > larger.  Why did the authors not try the initial random spikes in transit?
-> Fig. 3 I discussed in the major point above.  Code: Well written, a bit
-> under-commented, but clearly structured The easy installation of requirements
-> and use of CL options make the code very reusable and in general user-friendly
-> In lib.py, I am a bit puzzled about the way how the function "run_with_cache"
-> is defined. Why can't the run function be decorated with @mem.cache as for the
-> other functions?  Could the authors elaborate on the definition of V0 in line
-> 81 . It does not seem to be included in Table 1 or the main text.  On first run,
+> Fig. 3 I discussed in the major point above.
+
 > I got thrown a ton of FutureWarnings concerning the use of certain dtypes in
@@
 > warnings by using the Warnings library to ignore any FutureWarnings I then
-> performed the simulations using the --long option, which finished after 7h38m.
+> performed the simuluations using the --long option, which finished after 7h38m.

### 2018-03-09 code/main.py
correct ticks for the "detail" plot

@@ -209,10 +209,6 @@ def all_figs(short=True, quiet=False, dt=0.1*ms):
     fig4(linear=True, short=short, quiet=quiet, dt=dt,
          bias_correction=True, seed=main_seeds[5])
 
-    fig3_detail(linear=False, short=short, quiet=quiet, dt=1*ms,
-                seed=main_seeds[6])
-    fig3_detail(linear=False, short=short, quiet=quiet, dt=0.5*ms,
-                seed=main_seeds[6])
     fig3_detail(linear=False, short=short, quiet=quiet, dt=0.1*ms,
                 seed=main_seeds[6])
     fig3_detail(linear=False, short=short, quiet=quiet, dt=0.05*ms,

### 2018-03-09 article/Caze_2018.tex
Moving rebuttal and last version of tex
Add a (quick&dirty) supplement with the new figures

@@
 %}
+\clearpage
+\appendix
+\section*{Supplementary Figures}
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.33\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_gs100_mean_detail.pdf}
+\end{subfigure}%
+\begin{subfigure}[t]{0.33\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/grid_nl_dt_50us_gs100_mean_detail.pdf}
+\end{subfigure}
+\begin{subfigure}[t]{0.33\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/grid_nl_dt_10us_gs100_mean_detail.pdf}
+\end{subfigure}
+\caption{\label{fig:grid_detail}
+\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for non-linearly coupled networks simulated with different simulation time steps.} Color code as in Fig.~\ref{fig:grid}.
+Results are shown for a smaller range of connection strengths than in Fig.~\ref{fig:grid}.
+The total inhibitory connection strength was varied between \SI{24}{\milli\volt} and \SI{34.55}{\milli\volt}, the total excitatory connection strength was varied between \SI{34.91}{\milli\volt} and \SI{45.45}{\milli\volt}, i.e.
+the parameter range corresponds to a square region at the top of Fig.~\ref{fig:grid}B.
+Simulations where performed with simulation time steps of \SI{0.1}{\milli\second} (A; the value used for all other simulations shown), \SI{0.05}{\milli\second} (B), and \SI{0.01}{\milli\second} (C).}
+\end{figure}
 
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.5\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/markov_l_dt_100us_corrected.pdf}
+\end{subfigure}%
+\begin{subfigure}[t]{0.5\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/markov_nl_dt_100us_corrected.pdf}
+\end{subfigure}
+\caption{\label{fig:markov_corrected}
+\textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov}.
+The numerical solutions (grey lines and green squares) have been corrected by subtracting the background activity that is expected to occur by chance at every time step, i.e.
+the ``false positive'' spikes that are counted as being part of the synchronous spike.
+Background activity was estimated from the total activity before the stimulation with the synchronous pulse and, for a simulation time step of \SI{0.1}{\milli\second}, amounted to about 5.5 spikes per time step.}
+\end{figure}
 \end{document}

### 2018-03-09 article/Caze_2018.tex
minor changes in the main text

@@
 
+We added 1-50 spikes ``in transit'' to better match the results from the gridsearch. The spike ``in transit'' addition or substraction fail to modify the outcome.
+
 \begin{table}[ht]
@@
 We did not attempt to replicate the analytical solution for the evolution of synchronous pulses based on diffusion approximation (blue dots in Fig.~4 of \cite{Memmesheimer2012}).
-The article explains in more details the semi-analytical work that was more straightforward to reproduce.
+The original work explains in more details the semi-analytical work that was more straightforward to reproduce.
 To calculate the semi-analytical solutions for Fig.~\ref{fig:markov}, based on a numerical estimate of the distribution $P(V)$, we proceeded as follows.
@@
 Importantly, it strongly supports the original paper's main conclusion that non-linearly coupled networks have a large parameter range of stable propagation (i.e., blue-coloured points), while linearly coupled networks do not.
-The minor differences in our replication could be due to either our use of a clock-based simulation method, or to the slightly different initial conditions (no spikes ``in transit'').
+The minor differences in our replication could be due to either our use of a clock-based simulation method  (see Fig.~\ref{fig:grid_detail}), or to the slightly different initial conditions (no spikes ``in transit'').
 \begin{table}
@@
 The result of our simulation seems shifted upward compared to the original work.
-This difference is most visible at the origin of the plot.
+This difference becomes most visible at the origin of the plot.
+We corrected this shift (see Fig.~\ref{fig:markov_corrected}), but we still observe a small discrepency in the non-linear case.
 This might come from "false positive" spikes generated by the background activity (~5 spikes more in our simulation results).

### 2018-03-09 REBUTTAL.md
updated rebuttal text

@@
-We want to thank the reviewers for their well-intentioned and valuable
-comments. We describe, when needed, how we change the manuscript to adress
-their comments.
+We would like to again thank the reviewers for their valuable and constructive
+comments.
+
+In preparing the revision, we noticed an error in our plotting code. The network 
+firing rate plotted in Fig.1 (middle row) was incorrectly based on a bin size of
+0.1ms, instead of the 1ms that was used in the original publication (and also
+stated in our figure caption). Therefore, the (non-synchronous) background
+activity appeared to be 10 times lower than it actually was.
+
+Below we describe, when needed, how we changed the code and the manuscript to
+adress the reviewers' comments.
 
@@
 
-We modified the axis name to have full text inhibitory et excitatory
+We modified the axis labels accordingly.
 
@@
 > a and b, but was there a particular reason why it was omitted (e.g.
-> computation time)?  We added the third panel.
+> computation time)?
 
-We added the third panel
+There was no particular reason for this choice and we have now added the
+simulation and the corresponding plot to our Figure 2.
 
@@
 
-We modified the discussion accordingly (see L434 in the .tex file)
+We modified the discussion accordingly (see L434 in the .tex file).
 
@@
 
-The semi analytical work agrees with the original work. It's the numerical
-simulations that differ. (see L430)
+We have now clarified this in the text. The derivation is just provided as a
+more detailed description of the approach presented in the original article but
+is identical. There is a potential difference in the way the observed membrane
+potential distribution is used as an estimate of P(V), as the details (e.g.
+number of bins for the histogram, use of interpolation/smoothing, etc.) were not
+mentioned in the original article.
 
@@
 
-We corrected the text, the difference stems from the numerical simulation
-where the clocking introduce "false positive" spikes absent from a continuous
-model. The numerical curve are in fact shifted upwards due to false positve
-(see L430). This is due to false positive spikes.  The difference lays in how
-we sample the voltage distribution otherwise we did a similar computation. We
-acknowledge that details in the original work were unclear to reproduce the
-analytic approach (see L333)
+TODO: Things changed with the new correction
 
@@
 
-We further justify our choice (see L339 in tex file). The analytical was less
-explicitly described than the semi-analytical. We can contact the original
-authors to have further details. We were happy to reproduce at least on the
-approach, but we could try to have it reimplemented when we have further
-details.
+We now further justify our choice in the main text(see L339 in tex file). We
+found that the analytical approach was not described in as much detail as the
+semi-analytical one and therefore focussed on the latter. If the reviewers think
+that including the analytical solution is important, then we can contact the
+original authors to have further details.
 
@@
 
-We further explicit the differences from the original work (See L328).
-@stimberg should we change the figure.2?
+We have added some more quantitative comparison to the results in the original
+work (See L328).
 
@@
 
+TODO
+
 > The C panel from the original study has not been
@@
 > the area of unstable activity before stimulation seems to be significantly
-> larger.  Why did the authors not try the initial random spikes in transit?
-> Fig. 3 I discussed in the major point above.
+> larger.
+
+The C panel has now been replicated and we include further details about the
+quantitative differences to the original study.
+
+> Why did the authors not try the initial random spikes in transit?
+
+Our simulations now include initial random spikes, although the details of their
+implementation was not clear from the text. (See ...)
 
@@
 > used the requirements.txt to get the exact version numbers). I omitted the
-> warnings by using the Warnings library to ignore any FutureWarnings I then
-> performed the simuluations using the --long option, which finished after 7h38m.
+> warnings by using the Warnings library to ignore any FutureWarnings
+
+These warnings should only appear with numpy 1.14, which was released after the
+latest release of Brian 2. Please double check that you are using numpy 1.13.3
+as stated in requirements.txt. That said, the warnings can be safely ignored and
+Brian 2 does work correctly with numpy 1.14.

### 2018-03-09 REBUTTAL.md
Reply to a few more minor comments of Reviewer 2

@@
 more detailed description of the approach presented in the original article but
-is identical. There is a potential difference in the way the observed membrane
-potential distribution is used as an estimate of P(V), as the details (e.g.
-number of bins for the histogram, use of interpolation/smoothing, etc.) were not
-mentioned in the original article.
+is otherwise identical. There is a potential difference in the way the observed
+membrane potential distribution is used as an estimate of P(V), as the details
+(e.g. number of bins for the histogram, use of interpolation/smoothing, etc.)
+were not mentioned in the original article.
 
@@
 
+> In lib.py, I am a bit puzzled about the way how the function "run_with_cache" is defined. Why can't
+> the run function be decorated with `@mem.cache` as for the other functions?
+
+Functions that are to be used with joblib's Parallel/delayed mechanism cannot
+use the `@mem.cache` decorator directly (this is a known limitation of joblib
+and has to do with the inability of Python's pickle mechanism to pickle two
+functions that have the same name). We have now added a more detailed comment
+about this to the first time in `lib.py` where this occurs (the definition of
+`calc_group_evolution_cached`) and refer back to this comment for the other
+functions such as `run_with_cache`.
+
+> Could the authors elaborate on the definition of V0 in line 81. It does not seem to be included in 
+> Table 1 or the main text.
+
+V0 is the membrane potential displacement due to a constant input current. It
+is included in equation 1 and mentioned in the surrounding text, but its value
+was never mentioned. We now include it in Table 1.
+
 > The description for implementing the nonlinear networks could be rewritten to match closer the

### 2018-03-09 article/Caze_2018.tex
Manuscript updates

@@
 Dendritic non-linearities increase neurons' computation capacity, turning them into complex computing units \cite{Poirazi2003a}.
-However network studies are usually based on point neuron models that do not incorporate dendrites and their non-linearities.
+However, network studies are usually based on point neuron models that do not incorporate dendrites and their non-linearities.
 In contrast, the study replicated here \cite{Memmesheimer2012} uses a simple point-neuron model that contains an effective description of dendrites by a non-linear summation of its excitatory synaptic input.
@@
 The simulations in the original paper were done in phase representation, but our implementation uses the more standard representation in terms of the neurons' membrane potential.
-The membrane potential $V_i$ (measured relative to the resting potential) of neuron $i$ is described by (a slightly rewritten version equivalent to equation (1) of \cite{Memmesheimer2012}):
+The membrane potential $V_i$ of neuron $i$, measured relative to the resting potential, is described by:
 
 \begin{equation}
+\label{eq:neuron_model}
 \tau_m \frac{dV_i(t)}{dt} = - V_i(t) + V_0 + \sigma \left( \sum_{j\in E_i} w_\text{ex} \epsilon_{j}(t-\tau) \right) - \sum_{j \in I_i} w_\text{in}\epsilon_{j}(t-\tau),
@@
 The function $\epsilon_{j}$ is 1 whenever neuron $j$ spikes, and 0 otherwise.
+Equation~\ref{eq:neuron_model} is an alternative, mathematically equivalent formulation of equation (1) of \cite{Memmesheimer2012}.
 
@@
 The parameter values used in the original study as well as in our replication are summarized in Table~\ref{tab:parameters}.
-
-We added 1-50 spikes ``in transit'' to better match the results from the gridsearch. The spike ``in transit'' addition or substraction fail to modify the outcome.
 
@@
 \end{code}
+
+In addition to random initial conditions, i.e.
+random initial values of the membrane potential, the simulation includes 1--50 random spikes ``initially in transit''.
+The original article does not go into further details about their implementation, we decided to use the following: at the beginning of the simulation, a uniformly distributed number between 1 and 50 is drawn to determine the total number of initial spikes.
+These spikes are ``in transit'', meaning that they are modelled as arising from events before the start of the simulation.
+Since the synaptic delay in the network is \SI{5}{\milli\second}, we draw the arrival times for these spikes between \SI{0}{\milli\second} and \SI{5}{\milli\second}.
+Consistent with the probability for excitatory connections in the network ($p_\text{ex}=0.5$), we take half of these spikes as arising from excitatory and half from inhibitory sources, modelling there effect as described above.
+
 To facilitate simulation, we use the \emph{joblib} library to automatically store results and to distribute computation over processor cores.
@@
 For the grid search presented in Fig.~\ref{fig:grid}, we varied inhibitory and excitatory synaptic weights between \SI{0.16}{\milli\volt} and \SI{0.4}{\milli\volt} (given that each neuron receives on average 150 excitatory and 150 inhibitory inputs, this corresponds to a ``total weight'' between \SI{24}{\milli\volt} and \SI{60}{\milli\volt}, as used on the axes of Fig.~\ref{fig:grid}), using 100 steps for each variable (comparable to the 96 steps used in the original publication).
-Each network was simulated 10 times with different initial conditions (synaptic connections and initial membrane potential values), whereas the original publication used 20 simulations per weight combination and additionally added ``1--50 random spikes initially in transit''.
+Each network was simulated 10 times with different initial conditions (synaptic connections and initial membrane potential values), whereas the original publication used 20 simulations per weight combination.
 

### 2018-03-12 code/lib.py
Improved correction for Markov figure

@@ -21,17 +21,28 @@ def group_size_evolutions(group_size, n_rep=1, linear=True, dt=0.1*ms,
             seed = None
         else:
             seed = seeds[rep]
+        if bias_correction:
+            # Run without stimulation, but otherwise identical (same seed)
+            results_no_stim = run_with_cache(56 * ms, group_size=0,
+                                             stim_time=None, linear=linear,
+                                             repetition=rep, dt=dt, seed=seed)
         results = run_with_cache(56 * ms, group_size=group_size,
                                  stim_time=50 * ms, linear=linear,
                                  repetition=rep, dt=dt, seed=seed)
         next_iteration = np.sum(np.abs(results['t'] - 55 * ms) < dt / 2)
         if bias_correction:
-            spikes_before_stim = np.sum(results['t'] < 50*ms)
-            # Reduce the group size by the number of spikes that we'd expect
-            # by chance in a time step with the given background activity.
-            correction = spikes_before_stim / (50*ms/dt)
-            next_iteration -= correction
-        group_ev.append(next_iteration)
+            # Use the actual number of synchronous spike at the time of the
+            # stimulation -- due to the background activity, this is usually
+            # higher than the size of the stimulation group
+            g0 = np.sum(np.abs(results['t'] - 50 * ms) < dt / 2)
+            # Only count the synchronous spikes that were added due to the
+            # stimulation
+            next_iteration_no_stim = np.sum(np.abs(results_no_stim['t'] - 55 * ms) < dt / 2)
+            g1 = next_iteration - next_iteration_no_stim
+        else:
+            g0 = group_size
+            g1 = next_iteration
+        group_ev.append((g0, g1))
     return group_ev
 
 

### 2018-03-12 code/main.py

@@ -160,12 +160,14 @@ def fig4(linear=True, short=True, quiet=False, dt=0.1*ms, bias_correction=False,
     analytic_x = np.arange(1, 182, step_size)
     seeds = generate_seeds(seed, len(gsize_x)*n_rep + n_rep)
     # Numerical results
-    gsize = Parallel(n_jobs=-2)(delayed(group_size_evolutions)(i, n_rep=n_rep,
-                                                               linear=linear,
-                                                               dt=dt,
-                                                               seeds=seeds[idx*n_rep:(idx+1)*n_rep],
-                                                               bias_correction=bias_correction)
-                                for idx, i in enumerate(gsize_x))
+    results = Parallel(n_jobs=-2)(delayed(group_size_evolutions)(i, n_rep=n_rep,
+                                                                 linear=linear,
+                                                                 dt=dt,
+                                                                 seeds=seeds[idx*n_rep:(idx+1)*n_rep],
+                                                                 bias_correction=bias_correction)
+                                  for idx, i in enumerate(gsize_x))
+    g0 = [[result[0] for result in repetitions] for repetitions in results]
+    g1 = [[result[1] for result in repetitions] for repetitions in results]
     # Semi-analytical results
     seed_start = len(gsize_x)*n_rep
     result_list = Parallel(n_jobs=-2)(delayed(run_with_cache)(stim_time=None,
@@ -187,8 +189,8 @@ def fig4(linear=True, short=True, quiet=False, dt=0.1*ms, bias_correction=False,
     correction_string = '_corrected' if bias_correction else ''
     fname = "markov_%s_dt_%.0fus%s.pdf" % (coupling_string, dt/us, correction_string)
 
-    plot_markov(gsize_x, gsize, analytic_x, semi_analytic, linear=linear,
-                save=FIG_FOLDER + fname)
+    plot_markov(g0, g1, analytic_x, semi_analytic, linear=linear,
+                save=FIG_FOLDER + fname, bias_correction=bias_correction)
 
 
 def all_figs(short=True, quiet=False, dt=0.1*ms):

### 2018-03-12 code/plot.py

@@ -90,7 +90,8 @@ def plot_grid(par_range_exc, par_range_inh, colors, show_ylabel=True, save=None)
     save_fig(save, fig=fig)
 
 
-def plot_markov(group_x, group_ev, analytic_x, semi_analytic, save=None, linear=True):
+def plot_markov(group_x, group_ev, analytic_x, semi_analytic, save=None,
+                linear=True, bias_correction=False):
     """Plot the most probable evolution of a group size at time t+1 given the
     size at time t"""
     fig, ax = plt.subplots(gridspec_kw={'top': 0.95,
@@ -98,17 +99,18 @@ def plot_markov(group_x, group_ev, analytic_x, semi_analytic, save=None, linear=
                                         'left': 0.2,
                                         'right': 0.95})
     # Numeric solution
-    ax.set(aspect='equal', xticks=[1] + list(range(25, group_x[-1]+1, 25)),
-           yticks=list(range(0, group_x[-1]+1, 25)),
-           xlim=(-5, group_x[-1]+3.5/2), ylim=(-5, group_x[-1]+3.5/2),
-           xlabel="# of synchronized neurons $g'_0$",
-           ylabel="# of synchronized neurons $g'_1$")
+    g_symbol = '\hat{g}' if bias_correction else 'g'
+    ax.set(aspect='equal', xticks=[1] + list(range(25, np.max(group_x)+1, 25)),
+           yticks=list(range(0, np.max(group_x)+1, 25)),
+           xlim=(-5, np.max(group_x)+3.5/2), ylim=(-5, np.max(group_x)+3.5/2),
+           xlabel="# of synchronized neurons ${}'_0$".format(g_symbol),
+           ylabel="# of synchronized neurons ${}'_1$".format(g_symbol))
     ax.plot(group_x, np.array(group_ev), marker='_',
             ms=3.5,
             mew=1,
             color="black",
             linestyle='', alpha=0.2)
-    ax.plot(group_x,
+    ax.plot(np.mean(np.array(group_x), axis=1),
             np.mean(np.array(group_ev), axis=1),
             marker='s', color="lime",
             linestyle='')

### 2018-03-12 article/Caze_2018.tex
Various text changes (still incomplete)

@@
 random initial values of the membrane potential, the simulation includes 1--50 random spikes ``initially in transit''.
-The original article does not go into further details about their implementation, we decided to use the following: at the beginning of the simulation, a uniformly distributed number between 1 and 50 is drawn to determine the total number of initial spikes.
+The original article does not go into further details about their implementation, so we decided to use the following: at the beginning of the simulation, a uniformly distributed number between 1 and 50 is drawn to determine the total number of initial spikes.
 These spikes are ``in transit'', meaning that they are modelled as arising from events before the start of the simulation.
 Since the synaptic delay in the network is \SI{5}{\milli\second}, we draw the arrival times for these spikes between \SI{0}{\milli\second} and \SI{5}{\milli\second}.
-Consistent with the probability for excitatory connections in the network ($p_\text{ex}=0.5$), we take half of these spikes as arising from excitatory and half from inhibitory sources, modelling there effect as described above.
+Consistent with the probability for excitatory connections in the network ($p_\text{ex}=0.5$), we take half of these spikes as arising from excitatory and half from inhibitory sources, modelling their effect as described above.
 
@@
 
-For the grid search presented in Fig.~\ref{fig:grid}, we varied inhibitory and excitatory synaptic weights between \SI{0.16}{\milli\volt} and \SI{0.4}{\milli\volt} (given that each neuron receives on average 150 excitatory and 150 inhibitory inputs, this corresponds to a ``total weight'' between \SI{24}{\milli\volt} and \SI{60}{\milli\volt}, as used on the axes of Fig.~\ref{fig:grid}), using 100 steps for each variable (comparable to the 96 steps used in the original publication).
+For the grid search presented in Fig.~\ref{fig:grid}, we varied inhibitory and excitatory synaptic weights between \SI{0.16}{\milli\volt} and \SI{0.4}{\milli\volt}.
+Given that each neuron receives on average 150 excitatory and 150 inhibitory inputs, this corresponds to a ``total weight'' between \SI{24}{\milli\volt} and \SI{60}{\milli\volt}, as used on the axes of Fig.~\ref{fig:grid}).
+We used a resolution of 100 steps for each variable, comparable to the 96 steps used in the original publication.
 Each network was simulated 10 times with different initial conditions (synaptic connections and initial membrane potential values), whereas the original publication used 20 simulations per weight combination.
 
-Our replication present slight differences with the original grid search.
-The stable region surface ends up earlier in a regime with strong inhibitory connections.
-The odd blue-yellow-red region presents in the original article differs from the continuous transition we obtained in our simulations.
-Implementation details might explain these differences
-
 To numerically derive the evolution of synchronous pulse sizes presented in Fig.~\ref{fig:markov} (for the semi-analytical approach, see the next section), we performed simulations of \SI{56}{\milli\second} each.
-During each simulation, we stimulated the network at \SI{50}{\milli\second} with a synchronous pulse of activity, consisting of between 1 and 176 neurons (varied in steps of 5 -- the original study used group sizes between 1 and 181 varied in steps of 6).
+During each simulation, we stimulated the network at \SI{50}{\milli\second} with a synchronous pulse of activity, consisting of between 1 and 181 neurons (varied in steps of 5 -- the original study used group sizes in the same range varied in steps of 6).
 We then observed the number of active neurons at \SI{55}{\milli\second}, i.e.
@@
 \subsection*{Semi-analytical and analytical methods}
-We did not attempt to replicate the analytical solution for the evolution of synchronous pulses based on diffusion approximation (blue dots in Fig.~4 of \cite{Memmesheimer2012}).
-The original work explains in more details the semi-analytical work that was more straightforward to reproduce.
+We did not attempt to replicate the analytical solution for the evolution of synchronous pulses based on diffusion approximation (blue dots in Fig.~4 of \cite{Memmesheimer2012}), since the original publication did not give a detailed description of this approach.
+However, we replicate the semi-analytical work that was described in more detail.
+
 To calculate the semi-analytical solutions for Fig.~\ref{fig:markov}, based on a numerical estimate of the distribution $P(V)$, we proceeded as follows.
-First, we ran $2\times 50$ (once for the linear, once for the non-linear network) simulations of \SI{250}{\milli\second} each of a network with the default parameters but without any additional synchronous stimulation.
-We binned all membrane potential values over all time steps and neurons into 100 bins in the voltage interval $[-\Theta/8, \Theta]$, to obtain an estimate of $P(V)$, the distribution of the membrane potential.
-From this distribution we can estimate the probability $F$ that an additional input $\epsilon$ drives the neuron over its threshold (or equivalently, that the neuron is less than $\epsilon$ away from its threshold):
+First, we ran $2\times 50$ (once for the linear, once for the non-linear network) simulations of \SI{250}{\milli\second}.
+Each of these simulations was randomly connected and had random initial conditions, but received no additional synchronous stimulation.
+The original study additionally simulated each of the 100 networks 10 times, with the same synaptic connectivity but differing in the initial conditions.
+We then binned all membrane potential values over all time steps and neurons into 100 bins in the voltage interval $[-\Theta/8, \Theta]$ to obtain an estimate of $P(V)$, the distribution of the membrane potential.
+Note that the original study did not further specify how $P(V)$ was estimated from the simulation results.
+
+We then calculate the expected synchronous group size after one iteration as in the original publication.
+To make this calculation clearer, we now describe its derivation in detail.
+From the distribution $P(V)$ we can estimate the probability $F$ that an additional input $\epsilon$ drives the neuron over its threshold (or equivalently, that the neuron is less than $\epsilon$ away from its threshold):
 \begin{equation}
@@
 $\epsilon(n_\text{ex}, n_\text{in}) = \sigma(n_\text{ex}w_\text{ex}) + n_\text{in}w_\text{in}$.
-Let us assume that in the last iteration $g_i$ neurons spiked and that these neurons are refractory now, i.e.
+Let us assume that in the previous iteration $g_i$ neurons spiked and that these neurons are refractory now, i.e.
 that $N-g_i$ neurons are available to spike in this iteration.
@@
 \end{equation}
-In Fig.~\ref{fig:markov}, we plot the expected value of spiking neurons during the next iteration, i.e.:
+In Fig.~\ref{fig:markov}, we plot the expected value of spiking neurons during the next iteration, given a certain initial synchronous pulse $g_i'$:
 \begin{equation}
@@
 Combining individual results in this way does not necessarily lead to easily interpretable colours, but using a different scheme, e.g.
-colouring according to the class that occurred the most often, leads to visually similar results (not shown).
+colouring according to the class that occurred the most often, leads to visually similar results (Fig.~\ref{fig:grid_max}).
 
-Our replication does not reproduce all details of the original plots (in particular at the top of the plots), but looks very similar on a coarse scale.
-Importantly, it strongly supports the original paper's main conclusion that non-linearly coupled networks have a large parameter range of stable propagation (i.e., blue-coloured points), while linearly coupled networks do not.
-The minor differences in our replication could be due to either our use of a clock-based simulation method  (see Fig.~\ref{fig:grid_detail}), or to the slightly different initial conditions (no spikes ``in transit'').
 \begin{table}
@@
 
+Our replication does not reproduce all the quantitative details of the original plots.
+The parameter range where simulations are only unstable after they receive the synchronous stimulation (yellow) is smaller than in the original article.
+For linear networks, we do observe almost no simulations classified in this category, while the original article has a thin line of such classifications between the stable regime without propagation (green) and the regime where simulations are unstable even without stimulation (red).
+Similarly, in the original article the parameter exploration shows for each inhibitory connection weight a range of excitatory connection weights of about \SI{5}{\milli\volt} where the network is unstable only after the synchronous stimulation (yellow).
+In contrast, our simulations show a much smaller zone when the inhibitory connection strength is small (Fig.~\ref{fig:grid}B).
+It seems that these differences mostly stem from the fact that the transition to the regime where simulations are unstable without stimulation (red) happens for lower excitatory and higher inhibitory connection strength in our simulations than in the original article, i.e.
+that the red zone is shifted towards the bottom left.
+This is particularly evident for strong excitatory and inhibitory connections in non-linearly coupled networks (bottom right in Fig.~\ref{fig:grid}B and C) which are unstable in our simulations, but stable or only unstable after stimulation in the original publication.
+Finally, non-linearly coupled networks show a discontinuity for weak inhibitory connection strengths in the original publication.
+For increasing excitatory connection strengths, network behaviour goes from stable (blue) to unstable after stimulation (yellow) to unstable before stimulation (red), but then get classified again as stable (blue) in a small range of parameters before finally transitioning to unstable activity (yellow and red).
+We do not observe this in our simulations.
+
+Despite these differences, the qualitative network behaviour looks very similar on a coarse scale.
+Importantly, it strongly supports the original paper's main conclusion that non-linearly coupled networks have a large parameter range of stable propagation (i.e., blue-coloured points), while linearly coupled networks do not.
+The differences in our replication are most likely due to our use of a clock-based simulation method  (see Fig.~\ref{fig:grid_detail}).
+In principle, another reason could be implementation details of the initial ``spikes in transit'' that were not fully specified in the original article, but this seems unlikely as completely removing them did not change the results in a noticeable way (not shown).
+
 \begin{figure}
@@
 Blue colouring indicates stable propagation of synchrony, red indicates unstable background activity before onset of propagation, yellow indicates unstable background activity after onset of propagation, and green colouring indicates the absence of propagation (see Methods for details).\\
-Replication of Fig.~3a and b in \cite{Memmesheimer2012} (\url{https://doi.org/10.1371/journal.pcbi.1002384.g003})}
+Replication of Fig.~3 in \cite{Memmesheimer2012} (\url{https://doi.org/10.1371/journal.pcbi.1002384.g003})}
 \end{figure}
@@
 \caption{}\vspace{-1ex}
-\includegraphics[width=\textwidth]{Figs/markov_l_dt_100us.pdf}
+\includegraphics[width=\textwidth]{Figs/markov_l_dt_100us_corrected.pdf}
 \end{subfigure}%
@@
 \caption{}\vspace{-1ex}
-\includegraphics[width=\textwidth]{Figs/markov_nl_dt_100us.pdf}
+\includegraphics[width=\textwidth]{Figs/markov_nl_dt_100us_corrected.pdf}
 \end{subfigure}
-\caption{\label{fig:markov}
+\caption{\label{fig:markov_corrected}
 \textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks.} To numerically estimate the probability distribution, we show occurrences of pulse-sizes $g'_1$ in response to a pulse of size $g'_0$ by grey lines; green squares represent the corresponding mean response group sizes.\\
@@
 Finally, we looked at the evolution of synchronous group sizes for one combination of synaptic weights ($w_\text{ex}=w_\text{in}=\SI{0.2}{\milli\volt}$) in detail (Fig.~\ref{fig:markov}).
-The results confirms our previous conclusion that we can faithfully replicate the network behaviour.
-They match both qualitatively and quantitatively, the group size consistently declines with each iteration in linearly coupled networks (Fig.~\ref{fig:markov}A), whereas it increases for intermediate group sizes and declines otherwise in non-linearly coupled networks (Fig.~\ref{fig:markov}B).
-While the semi-analytic solution (red dotted line) shows a good match to the numerical results (grey lines, means as green dots), it shows some quantitative differences to the semi-analytic solution presented in Fig.~4 of the original article.
-The semi-analytical solution in the original article consistently overestimates the size of the group in the next iteration compared to the numerical solution.
-In contrast, our semi-analytical solution consistently underestimates their size in linearly coupled networks (Fig.~\ref{fig:markov}A).
-For non-linearly coupled networks, our solution underestimates the evolution of the group size for initial group sizes up to about 115--125 and only overestimates it for higher initial group sizes.
+The results confirms our previous conclusion that we can faithfully replicate the network behaviour which shows identical qualitative behaviour; the group size consistently declines with each iteration in linearly coupled networks (Fig.~\ref{fig:markov}A), whereas it increases for intermediate group sizes and declines otherwise in non-linearly coupled networks (Fig.~\ref{fig:markov}B).
+Quantitatively, the semi-analytical results also match well.
+Based on the plotted values in the original publication, the curve based on the semi-analytical solution crosses the identity line at about 85 ($G_1$) and 135 ($G_2$) for non-linearly coupled networks, peaking in between for $g'0\approx125$ and $g'1\approx139$.
+In our simulations, it crosses the line at about 86 and 134, and peaks at $g'0\approx126$ and $g'1\approx137$.
+As in the original article, our numerical results show slightly lower values for the group size in the next iteration, with the biggest difference for values around the peak of the function for non-linearly coupled networks (Fig.~\ref{fig:markov_corrected}B).
+However, we see a quantitative difference for low initial group sizes.
+In these simulations, the original publication shows a close match between the numerical results and the semi-analytical solution.
+In our simulation, we see %TODO
 
-The result of our simulation seems shifted upward compared to the original work.
-This difference becomes most visible at the origin of the plot.
-We corrected this shift (see Fig.~\ref{fig:markov_corrected}), but we still observe a small discrepency in the non-linear case.
-This might come from "false positive" spikes generated by the background activity (~5 spikes more in our simulation results).
-Yet our work strengthen the original result demonstrating a qualitative difference between linearly coupled and non-linearly coupled networks.
+To obtain this good quantitative match, we however add to apply a correction to the numerical results (for the uncorrected values, see Fig.~\ref{fig:markov}).
+The activity of the full network in the absence of stimulation is about \SI{55}{\kilo\hertz} (see Fig.~\ref{fig:raster}).
+Given that our simulation uses a time step of \SI{0.1}{\milli\second}, this means that at every time step about 5.5 neurons on average are synchronously active.
+When we stimulate a network with a pulse of $g'_0$ synchronous neurons, the actual number of synchronously active neurons is therefore higher than this stimulation.
+Similarly, we have to correct the size of the observed group in the next iteration.
+In contrast to the simulation strategy of the original publication that could make use of an ``infinite precision'' to detect synchronous spikes triggered by the stimulation, our simulation will also detect all the synchronous spikes resulting from the background activity.
+In the corrected values shown in Fig.~\ref{fig:markov_corrected} we therefore used the actually observed synchronous spikes $\hat{g}'_0 \geq g'_0$ at the time of the stimulation, and the number of added spikes due to the stimulation $\hat{g}'_1 = g'_{1 \text{stim}} - g'_{1 \text{no stim}}$.
+Note that the latter correction slightly ``overcorrects'', as it discards all spikes that are resulting from background activity, even those that also would have been triggered by the stimulation.
+
+Despite the small quantitative differences, our work strengthens the original result demonstrating a qualitative difference between linearly coupled and non-linearly coupled networks.
 
@@
 \section*{Supplementary Figures}
-\begin{figure}
+\begin{figure}[h]
+\centering
+\begin{subfigure}[t]{0.33\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/grid_l_dt_100us_gs100.pdf}
+\end{subfigure}%
+\begin{subfigure}[t]{0.33\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_gs100.pdf}
+\end{subfigure}
+\begin{subfigure}[t]{0.33\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_gs75.pdf}
+\end{subfigure}
+\caption{\label{fig:grid_max}
+\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for linearly (A) and non-linearly (B, C) coupled networks.} All conventions as in Fig.~\ref{fig:grid}, but points are coloured according the observed qualitative behaviour that occurred the most often among the 10 independent simulations for given connection strengths.}
+\end{figure}
+
+\begin{figure}[h]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[h]
 \centering
@@
 \caption{}\vspace{-1ex}
-\includegraphics[width=\textwidth]{Figs/markov_l_dt_100us_corrected.pdf}
+\includegraphics[width=\textwidth]{Figs/markov_l_dt_100us.pdf}
 \end{subfigure}%
@@
 \caption{}\vspace{-1ex}
-\includegraphics[width=\textwidth]{Figs/markov_nl_dt_100us_corrected.pdf}
+\includegraphics[width=\textwidth]{Figs/markov_nl_dt_100us.pdf}
 \end{subfigure}
-\caption{\label{fig:markov_corrected}
+\caption{\label{fig:markov}
 \textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov}.
-The numerical solutions (grey lines and green squares) have been corrected by subtracting the background activity that is expected to occur by chance at every time step, i.e.
-the ``false positive'' spikes that are counted as being part of the synchronous spike.
-Background activity was estimated from the total activity before the stimulation with the synchronous pulse and, for a simulation time step of \SI{0.1}{\milli\second}, amounted to about 5.5 spikes per time step.}
+Without correction (see text)}
 \end{figure}

### 2018-03-12 article/Caze_2018.tex
More text changes

@@
 The originality of this model lays in a filtering of the excitatory inputs by the function $\sigma$ to model dendritic non-linearities.
-The study considers two functions $\sigma$ (see Fig.~1 of the original paper and insets in Fig.~\ref{fig:markov}).
+The study considers two functions $\sigma$ (see Fig.~1 of the original paper and insets in Fig.~\ref{fig:markov_corrected}).
 Linear coupling, defined by $\sigma(x)=x$, and non-linear coupling with:
@@
 to re-use an old result obtained with an outdated version of the code) while keeping the code readable.
-To reduce the total simulation time, the grid exploration in Fig.~\ref{fig:grid}, and the analysis of group size evolution in Fig.~\ref{fig:markov} have been distributed over processor cores using joblib's \verb|Parallel| construct.
-For the simulations presented in Fig.~\ref{fig:grid}, multiple repetitions for the same combination of synaptic weights are distributed over processor cores, for the simulations presented in Fig.~\ref{fig:markov}, simulations are evaluated in parallel over group sizes.
+To reduce the total simulation time, the grid exploration in Fig.~\ref{fig:grid}, and the analysis of group size evolution in Fig.~\ref{fig:markov_corrected} have been distributed over processor cores using joblib's \verb|Parallel| construct.
+For the simulations presented in Fig.~\ref{fig:grid}, multiple repetitions for the same combination of synaptic weights are distributed over processor cores, for the simulations presented in Fig.~\ref{fig:markov_corrected}, simulations are evaluated in parallel over group sizes.
 In both cases, a number of $C-1$ parallel processes is used, where $C$ is the number of processor cores in the user's system.
@@
 
-To numerically derive the evolution of synchronous pulse sizes presented in Fig.~\ref{fig:markov} (for the semi-analytical approach, see the next section), we performed simulations of \SI{56}{\milli\second} each.
+To numerically derive the evolution of synchronous pulse sizes presented in Fig.~\ref{fig:markov_corrected} (for the semi-analytical approach, see the next section), we performed simulations of \SI{56}{\milli\second} each.
 During each simulation, we stimulated the network at \SI{50}{\milli\second} with a synchronous pulse of activity, consisting of between 1 and 181 neurons (varied in steps of 5 -- the original study used group sizes in the same range varied in steps of 6).
@@
 For each stimulation group size, we ran the simulations 50~times with different initial conditions, consistent with the original study.
+To achieve a better quantitative match with the original study, we applied a correction for the stimulation group size $g'_0$ and the observed group size $g'_1$ in the next iteration (for the uncorrected results, see Fig.~\ref{fig:markov}).
+We refer to the corrected values as $\hat{g}_0$ and $\hat{g}_1$, respectively.
+These corrections are necessary because of the background activity and our clock-based simulation method and are motivated as follows.
+The activity of the full network in the absence of stimulation is about \SI{55}{\kilo\hertz} (see Fig.~\ref{fig:raster}).
+Given that our simulation uses a time step of \SI{0.1}{\milli\second}, this means that at every time step about 5.5 neurons on average are synchronously active.
+When we stimulate a network with a pulse of $g'_0$ synchronous neurons, the actual number of synchronously active neurons is therefore higher than this stimulation.
+Similarly, we have to correct the size of the observed group in the next iteration.
+In contrast to the simulation strategy of the original publication that could make use of an ``infinite precision'' to detect synchronous spikes triggered by the stimulation, our simulation will also detect all the synchronous spikes resulting from the background activity.
+In the corrected values shown in Fig.~\ref{fig:markov_corrected} we therefore used the actually observed synchronous spikes $\hat{g}'_0 \geq g'_0$ at the time of the stimulation, and the number of added spikes due to the stimulation $\hat{g}'_1 = g'_{1 \text{stim}} - g'_{1 \text{no stim}}$, where $g'_{1 \text{stim}}$ is the number of synchronous spikes we observe in a network with stimulation, and $g'_{1 \text{no stim}}$ the number of observed spikes in a network without stimulation.
+Both networks are simulated with the same random seed and therefore have the same network connectivity and the same initial conditions; the only difference lies in the presence or absence of external synchronous stimulation.
+Note that the correction for $g'_1$ slightly ``overcorrects'', as it discards all spikes that are resulting from background activity, even those that also would have been triggered by the stimulation.
 
@@
 
-To calculate the semi-analytical solutions for Fig.~\ref{fig:markov}, based on a numerical estimate of the distribution $P(V)$, we proceeded as follows.
+To calculate the semi-analytical solutions for Fig.~\ref{fig:markov_corrected}, based on a numerical estimate of the distribution $P(V)$, we proceeded as follows.
 First, we ran $2\times 50$ (once for the linear, once for the non-linear network) simulations of \SI{250}{\milli\second}.
@@
 \end{equation}
-In Fig.~\ref{fig:markov}, we plot the expected value of spiking neurons during the next iteration, given a certain initial synchronous pulse $g_i'$:
+In Fig.~\ref{fig:markov_corrected}, we plot the expected value of spiking neurons during the next iteration, given a certain initial synchronous pulse $g_i'$:
 \begin{equation}
@@
 
-Finally, we looked at the evolution of synchronous group sizes for one combination of synaptic weights ($w_\text{ex}=w_\text{in}=\SI{0.2}{\milli\volt}$) in detail (Fig.~\ref{fig:markov}).
-The results confirms our previous conclusion that we can faithfully replicate the network behaviour which shows identical qualitative behaviour; the group size consistently declines with each iteration in linearly coupled networks (Fig.~\ref{fig:markov}A), whereas it increases for intermediate group sizes and declines otherwise in non-linearly coupled networks (Fig.~\ref{fig:markov}B).
+Finally, we looked at the evolution of synchronous group sizes for one combination of synaptic weights ($w_\text{ex}=w_\text{in}=\SI{0.2}{\milli\volt}$) in detail (Fig.~\ref{fig:markov_corrected}).
+The results confirms our previous conclusion that we can faithfully replicate the network behaviour which shows identical qualitative behaviour; the group size consistently declines with each iteration in linearly coupled networks (Fig.~\ref{fig:markov_corrected}A), whereas it increases for intermediate group sizes and declines otherwise in non-linearly coupled networks (Fig.~\ref{fig:markov_corrected}B).
 Quantitatively, the semi-analytical results also match well.
-Based on the plotted values in the original publication, the curve based on the semi-analytical solution crosses the identity line at about 85 ($G_1$) and 135 ($G_2$) for non-linearly coupled networks, peaking in between for $g'0\approx125$ and $g'1\approx139$.
-In our simulations, it crosses the line at about 86 and 134, and peaks at $g'0\approx126$ and $g'1\approx137$.
+Based on the plotted values in the original publication (Fig.~4 in \cite{Memmesheimer2012}), the curve based on the semi-analytical solution crosses the identity line at about 85 ($G_1$) and 135 ($G_2$) for non-linearly coupled networks, peaking in between for $g'_0\approx125$ and $g'_1\approx139$.
+In our simulations, it crosses the line at about 86 and 134, and peaks at $g'_0\approx126$ and $g'_1\approx137$.
 As in the original article, our numerical results show slightly lower values for the group size in the next iteration, with the biggest difference for values around the peak of the function for non-linearly coupled networks (Fig.~\ref{fig:markov_corrected}B).
@@
 In these simulations, the original publication shows a close match between the numerical results and the semi-analytical solution.
-In our simulation, we see %TODO
-
-To obtain this good quantitative match, we however add to apply a correction to the numerical results (for the uncorrected values, see Fig.~\ref{fig:markov}).
-The activity of the full network in the absence of stimulation is about \SI{55}{\kilo\hertz} (see Fig.~\ref{fig:raster}).
-Given that our simulation uses a time step of \SI{0.1}{\milli\second}, this means that at every time step about 5.5 neurons on average are synchronously active.
-When we stimulate a network with a pulse of $g'_0$ synchronous neurons, the actual number of synchronously active neurons is therefore higher than this stimulation.
-Similarly, we have to correct the size of the observed group in the next iteration.
-In contrast to the simulation strategy of the original publication that could make use of an ``infinite precision'' to detect synchronous spikes triggered by the stimulation, our simulation will also detect all the synchronous spikes resulting from the background activity.
-In the corrected values shown in Fig.~\ref{fig:markov_corrected} we therefore used the actually observed synchronous spikes $\hat{g}'_0 \geq g'_0$ at the time of the stimulation, and the number of added spikes due to the stimulation $\hat{g}'_1 = g'_{1 \text{stim}} - g'_{1 \text{no stim}}$.
-Note that the latter correction slightly ``overcorrects'', as it discards all spikes that are resulting from background activity, even those that also would have been triggered by the stimulation.
+In our simulation, the semi-analytical solution overestimates the numerical one.
+Be reminded that to obtain this good quantitative match, we however had to apply a correction to the numerical results, as explained in the implementation section (for the uncorrected values, see Fig.~\ref{fig:markov}).
 
@@
 \textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for non-linearly coupled networks simulated with different simulation time steps.} Color code as in Fig.~\ref{fig:grid}.
-Results are shown for a smaller range of connection strengths than in Fig.~\ref{fig:grid}.
+Results are shown for a smaller range of connection strengths than in Fig.~\ref{fig:grid}, and only for non-linearly coupled networks with an synchronous stimulation of 100 neurons.
 The total inhibitory connection strength was varied between \SI{24}{\milli\volt} and \SI{34.55}{\milli\volt}, the total excitatory connection strength was varied between \SI{34.91}{\milli\volt} and \SI{45.45}{\milli\volt}, i.e.
 the parameter range corresponds to a square region at the top of Fig.~\ref{fig:grid}B.
-Simulations where performed with simulation time steps of \SI{0.1}{\milli\second} (A; the value used for all other simulations shown), \SI{0.05}{\milli\second} (B), and \SI{0.01}{\milli\second} (C).}
+Simulations where performed with simulation time steps of \SI{0.1}{\milli\second} (A; also the value used for all other simulations shown), \SI{0.05}{\milli\second} (B), and \SI{0.01}{\milli\second} (C).}
 \end{figure}
@@
 \caption{\label{fig:markov}
-\textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov}.
+\textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_correction}.
 Without correction (see text)}

### 2018-03-13 article/Caze_2018.tex
Plot raster plot with different dt's for high connection strengths, various changes to text

@@
 This is particularly evident for strong excitatory and inhibitory connections in non-linearly coupled networks (bottom right in Fig.~\ref{fig:grid}B and C) which are unstable in our simulations, but stable or only unstable after stimulation in the original publication.
+Simulating the parameter combination corresponding to the point in the bottom right corner of the plot different time resolutions (Fig.~\ref{fig:raster_strong}), we find that this difference does indeed seem to be triggered by limited time resolution in the model.
+The forced synchronisation of all spikes to a grid of \SI{0.1}{\milli\second}, together with the homogeneity of the synaptic delays, leads to strong oscillations in our simulation (Fig.~\ref{fig:raster_strong}A), which is consequently classified as unstable.
+When we use a simulation time step of \SI{0.01}{\milli\second}, these osciallations disappear and the network activity therefore gets classified as ``stable without persistent propagation''.
 Finally, non-linearly coupled networks show a discontinuity for weak inhibitory connection strengths in the original publication.
 For increasing excitatory connection strengths, network behaviour goes from stable (blue) to unstable after stimulation (yellow) to unstable before stimulation (red), but then get classified again as stable (blue) in a small range of parameters before finally transitioning to unstable activity (yellow and red).
-We do not observe this in our simulations.
+We do not observe this in our simulations, but simulations with a finer time resolution (Fig.~\ref{fig:grid_detail}C) indicate that this difference could be caused by the limited time resolution of our simulations as well.
 
@@
 Importantly, it strongly supports the original paper's main conclusion that non-linearly coupled networks have a large parameter range of stable propagation (i.e., blue-coloured points), while linearly coupled networks do not.
-The differences in our replication are most likely due to our use of a clock-based simulation method  (see Fig.~\ref{fig:grid_detail}).
-In principle, another reason could be implementation details of the initial ``spikes in transit'' that were not fully specified in the original article, but this seems unlikely as completely removing them did not change the results in a noticeable way (not shown).
+The differences in our replication are most likely due to our use of a clock-based simulation method with a limited time resolution (see Fig.~\ref{fig:grid_detail} and Fig.~\ref{fig:raster_strong}).
+In principle, another reason could be implementation details of the initial ``spikes in transit'' that were not fully specified in the original article, but this seems unlikely since completely removing them did not change the results in a noticeable way (not shown).
 
@@
 We managed to qualitatively reproduce the main results of Raoul-Martin Memmes\-heimer and Marc Timme \cite{Memmesheimer2012} despite some slight quantitative differences.
-The grid search differs in certain regions and the markov analysis demonstrate a slight shifth upward for the numerical results.
-These difference could be due to our use of clock-based instead of event-driven simulations, as it forces all activity to a temporal grid of finite precision.
-We tried finer (\SI{0.05}{\milli\second}) and coarser (\SI{0.2}{\milli\second}, \SI{0.5}{\milli\second}) temporal resolutions and obtained qualitatively the same results (not shown).
-Another potential source for the differences is that our initial conditions do not include spikes ``in transit'' at the start of the simulation, which might further contribute to the quantitative differences we see.
+The grid search over parameters showed a higher prevalence of networks with unstable activity before the onset of stimulation compared to the original study.
+In the analysis of the evolution of synchronous pulses of different sizes, our results need a correction for the use of a clock-based simulation method to show a good quantative match with the original results.
+However, a marked difference remains for small initial group sizes.
+The differences we see are most likely due to our use of a clock-based instead of event-driven simulations, as it forces all activity to a temporal grid of finite precision.
+However, the main qualitative finding---non-linearly coupled networks have a large parameter range supporting persistent propagation of synchronous activity whereas linearly coupled networks do not---remains if we use finer (\SI{0.05}{\milli\second}) or coarser (\SI{0.2}{\milli\second}, \SI{0.5}{\milli\second}) temporal resolutions (data not shown).
 
@@
 
+\begin{figure}
+\centering
+\begin{subfigure}[t]{0.5\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/spikes_nl_strong_dt_100us.pdf}
+\end{subfigure}%
+\begin{subfigure}[t]{0.5\textwidth}
+\caption{}\vspace{-1ex}
+\includegraphics[width=\textwidth]{Figs/spikes_nl_strong_dt_10us.pdf}
+\end{subfigure}
+\caption{\label{fig:raster_strong}
+\textbf{Propagation of synchronous spiking in non-linearly coupled networks with strong recurrent connections when simulated with a time step of \SI{0.1}{\milli\second} (A), or \SI{0.01}{\milli\second} (B).} All conventions as in Fig.~\ref{fig:raster}, but for strong recurrent connections ($w_\text{ex} = w_\text{in} = \SI{0.4}{\milli\volt}$).
+Both simulated networks use non-linearly coupling, the network shown in panel (B) is simulated with a 10-times finer temporal resolution compared to the other results shown.}
+\end{figure}
+
 \begin{figure}[h]
@@
 \caption{\label{fig:markov}
-\textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_correction}.
-Without correction (see text)}
+\textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_corrected}.
+The numerical results shown here (gray lines and green squares) are not corrected for the bias introduced by the clock-driven integration method (see text for details).}
 \end{figure}

### 2018-03-13 code/lib.py

@@ -14,7 +14,11 @@ mem = Memory(cachedir='./__joblib_cache__', verbose=0, compress=True)
 
 def group_size_evolutions(group_size, n_rep=1, linear=True, dt=0.1*ms,
                           bias_correction=False, seeds=None):
-    """Return the evolution of the group size after one cycle"""
+    """Return the evolution of the group size after one cycle. Returns a
+    tuple (g0, g1), containing the size of the group size at stimulation time
+    (g0), and the group size in the next iteration (g1). If ``bias_correction``
+    is set to True, both of these values are corrected for the bias introduced
+    by the finite time step size."""
     group_ev = []
     for rep in range(n_rep):
         if seeds is None:
@@ -53,6 +57,8 @@ def F(bins, v_hist, epsilon):
 
 
 def epsilon(n_ex, n_in, w_ex, w_in, linear=True):
+    """Total input for a neuron with given number of connections and given
+       connection weights."""
     in_input = -n_in*w_in
     ex_input = n_ex*w_ex
     if not linear:
@@ -62,6 +68,8 @@ def epsilon(n_ex, n_in, w_ex, w_in, linear=True):
 
 
 def P_conn(group_size, n_ex, n_in, p_0, p_ex, p_in):
+    """Probability that a neuron receives exactly n_ex excitatory and n_in
+       inhibitory connections."""
     n_remain = group_size - n_ex - n_in
     return (comb(group_size, n_ex+n_in, exact=True) * comb(n_ex+n_in, n_ex, exact=True) *
             (p_0*p_ex)**n_ex * (p_0*p_in)**n_in * (1 - p_0)**n_remain)
@@ -364,4 +372,3 @@ def decide_color(results, method='max'):
                         persistent], dtype=float)/total
     else:
         raise AssertionError('Unkown method: %s' % method)
-

### 2018-03-13 code/main.py

@@ -19,8 +19,8 @@ br2.prefs.codegen.target = 'cython'
 
 FIG_FOLDER = "../article/Figs/"
 
-main_seeds = [3982293089, 1861487226, 2570878100, 3472600360, 2780156760,
-              1966509933, 1687607157]
+main_seeds = [29732904, 94614906, 1861487226, 2570878100, 3472600360, 2780156760,
+              1966509933, 1687607157, 238607587]
 
 if not os.path.exists(FIG_FOLDER):
     os.makedirs(FIG_FOLDER)
@@ -34,33 +34,48 @@ def generate_seeds(main_seed, n_seeds):
     return np.random.randint(0, 2**32-1, size=n_seeds, dtype=np.uint32)
 
 
-def fig2(quiet=False, dt=0.1*ms, seed=None):
+def fig2(linear=True, quiet=False, dt=0.1*ms, seed=None):
     """Generate the raster plot and population statistics for Figure 2
     of the original paper (https://doi.org/10.1371/journal.pcbi.1002384.g002)"""
     if not quiet:
-        print('Running simulations for Figure 2')
-    seeds = generate_seeds(seed, 2)
-    results = run_with_cache(w_ex=0.2*mV, w_in=0.2*mV, linear=True, dt=dt,
-                             seed=seeds[0])
-    results_nl = run_with_cache(w_ex=0.2*mV, w_in=0.2*mV, linear=False, dt=dt,
-                                seed=seeds[1])
+        coupling = 'linear' if linear else 'non-linear'
+        print('Running simulations for Figure 2 ({} coupling)'.format(coupling))
+    results = run_with_cache(w_ex=0.2*mV, w_in=0.2*mV, linear=linear, dt=dt,
+                             seed=seed)
 
-    figname = "spikes_l_dt_%.0fus.pdf" % (dt/us)
+    if linear:
+        figname = "spikes_l_dt_%.0fus.pdf" % (dt/us)
+    else:
+        figname = "spikes_nl_dt_%.0fus.pdf" % (dt / us)
     plot_population_activity(results, save=FIG_FOLDER + figname, dt=dt)
-    figname = "spikes_nl_dt_%.0fus.pdf" % (dt/us)
-    plot_population_activity(results_nl, save=FIG_FOLDER + figname, dt=dt)
 
 
- 
+def fig2_strong_connections(linear=True, quiet=False, dt=0.1*ms, seed=None):
+    """Generate a raster plot and population statistics similar to Figure 2
[…]

### 2018-03-13 article/Caze_2018.tex
update the ve wording

@@
 \end{cases}
+\label{eq:non-linear}
 \end{equation}
@@
 
-For non-linearly coupled networks, we have to use a slightly more complicated approach where we sum up all the received excitatory input in a variable \verb|ve|, apply the non-linear function $\sigma$ to this input, and then reset the variable \verb|ve| back to 0 to prepare for the next time step.
+We used a the predefined \verb|clip| function to implemented non-linear coupling into a network. The function clips a value to a given range, following the syntax
+\begin{code}
+clip(value, lower_bound, upper_bound)
+\end{code}
+
+We employed this functions on the received excitatory inputs stored in a placed holder variable \verb|ve|.
+The variable corresponds to x in eq.~\ref{eq:non-linear}.
+We then reset the variable \verb|ve| back to 0 to prepare for the next time step.
 In Brian syntax (the definition of the inhibitory synapses is identical to the linearly coupled network):
+
 \begin{code}
@@
 \end{code}
-The \verb|run_regularly| operation that is run every time step to implement the non-linear $\sigma$ function refers to the predefined \verb|clip| function which clips the value to a given range, following the syntax
-\begin{code}
-clip(value, lower_bound, upper_bound)
-\end{code}
+
+The \verb|run_regularly| operation enables that to run the non-linear summation between every time steps.
 
@@
 \caption{\label{fig:grid_max}
-\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for linearly (A) and non-linearly (B, C) coupled networks.} All conventions as in Fig.~\ref{fig:grid}, but points are coloured according the observed qualitative behaviour that occurred the most often among the 10 independent simulations for given connection strengths.}
+\textbf{Using max instead of mean to color each pixels.} All conventions as in Fig.~\ref{fig:grid}, but points are coloured according the observed qualitative behaviour that occurred the most often among the 10 independent simulations for given connection strengths.}
 \end{figure}
@@
 \caption{\label{fig:grid_detail}
-\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for non-linearly coupled networks simulated with different simulation time steps.} Color code as in Fig.~\ref{fig:grid}.
+\textbf{Zoom on qualitative network behaviour with different simulation time steps.} Color code as in Fig.~\ref{fig:grid}.
 Results are shown for a smaller range of connection strengths than in Fig.~\ref{fig:grid}, and only for non-linearly coupled networks with an synchronous stimulation of 100 neurons.
@@
 \caption{\label{fig:raster_strong}
-\textbf{Propagation of synchronous spiking in non-linearly coupled networks with strong recurrent connections when simulated with a time step of \SI{0.1}{\milli\second} (A), or \SI{0.01}{\milli\second} (B).} All conventions as in Fig.~\ref{fig:raster}, but for strong recurrent connections ($w_\text{ex} = w_\text{in} = \SI{0.4}{\milli\volt}$).
+\textbf{Propagation of synchronous spiking when simulated with small timesteps}.(A) Time step of \SI{0.1}{\milli\second}, or \SI{0.01}{\milli\second} (B) All conventions as in Fig.~\ref{fig:raster}, but for strong recurrent connections ($w_\text{ex} = w_\text{in} = \SI{0.4}{\milli\volt}$).
 Both simulated networks use non-linearly coupling, the network shown in panel (B) is simulated with a 10-times finer temporal resolution compared to the other results shown.}
@@
 \caption{\label{fig:markov}
-\textbf{Evolution of synchronous pulses in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_corrected}.
+\textbf{Evolution of synchronous pulses when using smaller timesteps in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_corrected}.
 The numerical results shown here (gray lines and green squares) are not corrected for the bias introduced by the clock-driven integration method (see text for details).}

### 2018-03-13 REBUTTAL.md
Update REBUTTAL.md
First TODO checked
Update REBUTTAL.md
Address the second todo (next commit I changed the tex)
Update REBUTTAL.md
The new main figure.2 is the corrected one.

@@
 
-We have now clarified this in the text. The derivation is just provided as a
+We clarified this in the text. The derivation is just provided as a
 more detailed description of the approach presented in the original article but
@@
 
-TODO: Things changed with the new correction
+We added a redone the main figure (fig.2) and added a supplemental figure without correction (fig.7) and we discussed further the difference between the semi-analytical result and the numerical one (L430)
 
@@
 
-TODO
+We rewrote given reviewers recommendations. (see L311)
 
@@
 Our simulations now include initial random spikes, although the details of their
-implementation was not clear from the text. (See ...)
+implementation was not clear from the text.
 

### 2018-03-13 article/Caze_2018.tex
correcting last supp figure

@@
 \caption{\label{fig:markov}
-\textbf{Evolution of synchronous pulses when using smaller timesteps in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_corrected}.
+\textbf{Evolution of synchronous pulses without correction in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_corrected}.
 The numerical results shown here (gray lines and green squares) are not corrected for the bias introduced by the clock-driven integration method (see text for details).}

### 2018-03-13 article/Caze_2018.tex
correcting last supp figure again

@@
 \caption{\label{fig:markov}
-\textbf{Evolution of synchronous pulses without correction in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_corrected}.
+\textbf{Evolution of synchronous pulses without correction in linearly (A) and non-linearly (B) coupled networks.} All conventions as in Fig.~\ref{fig:markov_corrected}.
 The numerical results shown here (gray lines and green squares) are not corrected for the bias introduced by the clock-driven integration method (see text for details).}

### 2018-03-13 REBUTTAL.md
update rebuttal file

--- 2018-03-09 REBUTTAL.md
@@
 We would like to again thank the reviewers for their valuable and constructive
-comments.
+comments. We have updated the code and the manuscript, and additionally
+added a file `Caze_2018_diff.pdf` which shows the changes in the manuscript
+(changes in the figures are not always well presented, but the document should
+give a good overview of which parts of the text have changed).
 
@@
 
-# RW1
+## Reviewer 1 (@pietromarchesi)
 
@@
 
-We modified the discussion accordingly (see L434 in the .tex file).
+We modified the discussion accordingly (see L451 in the .tex file).
 
@@
 
-We have now clarified this in the text. The derivation is just provided as a
-more detailed description of the approach presented in the original article but
-is otherwise identical. There is a potential difference in the way the observed
-membrane potential distribution is used as an estimate of P(V), as the details
-(e.g. number of bins for the histogram, use of interpolation/smoothing, etc.)
-were not mentioned in the original article.
+We clarified this in the text (see L345 in the .tex file). The derivation is
+just provided as a more detailed description of the approach presented in the
+original article but is otherwise identical. There is a potential difference in
+the way the observed membrane potential distribution is used as an estimate of
+P(V), as the details (e.g. number of bins for the histogram, use of
+interpolation/smoothing, etc.) were not mentioned in the original article.
 
@@
 
-TODO: Things changed with the new correction
+We have added a new paragraph to the text (see L338 in the .tex file) that
+introduces a correction to the plotted values, bringing the numerical results
+into closer agreement with the original study. Figure 3 has been updated
+accordingly and the previous version of the figure (without the correction) has
+been added as a supplementary figure (Figure 7). We have also added more
+discussion of the quantitative differences between our results and the original
+study (L444 in the .tex file).
 
-# RW2
+## Reviewer 2 (@degoldschmidt)
 
-## Major issue:
+### Major issue:
 
@@
 
-We now further justify our choice in the main text(see L339 in tex file). We
+We now further justify our choice in the main text (see L339 in .tex file). We
 found that the analytical approach was not described in as much detail as the
@@
 We have added some more quantitative comparison to the results in the original
-work (See L328).
+work for Figure 2 (See L423 in the .tex file) and Figure 3 (see L444 in the .tex
+file), as well as an extended discussion of the source of the differences via
+the additional simulations presented in the supplementary Figures 5 and 6.
 
-## Minor issues
+### Minor issues
+We have corrected the typographical issues (spaces, commas, etc.) as suggested
+by the reviewer, as well as rewritten several sentences to make them more clear
+and to avoid parentheses. We have also aligned xticks/yticks with the values
+used in the original publication.
 
-> In lib.py, I am a bit puzzled about the way how the function "run_with_cache" is defined. Why can't
-> the run function be decorated with `@mem.cache` as for the other functions?
+> In lib.py, I am a bit puzzled about the way how the function "run_with_cache"
+> is defined. Why can't the run function be decorated with `@mem.cache` as for
+> the other functions?
 
@@
 
-> Could the authors elaborate on the definition of V0 in line 81. It does not seem to be included in 
-> Table 1 or the main text.
+> Could the authors elaborate on the definition of V0 in line 81. It does not
+> seem to be included in Table 1 or the main text.
 
@@
 
-TODO
+We rewrote the text according to the reviewer's recommendations (see L311 in the .tex file)
 
@@
 The C panel has now been replicated and we include further details about the
-quantitative differences to the original study.
+quantitative differences to the original study (See L423 in the .tex file).
 

### 2018-05-14 article/Caze_2018.tex
Updated editing information

@@
 \fancyfoot[R]{\sffamily Jan 2018 $\vert$
-                        Volume \textbf{1} $\vert$
+                        Volume \textbf{4} $\vert$
                         Issue \textbf{1}}
@@
   {\bfseries Editor}\\
-  Name Surname\\
+  Nicolas P. Rougier\\
 
   {\bfseries Reviewers}\\
-        Name Surname\\
-        Name Surname\\
+        Pietro Marchesi\\
+        Dennis Goldschmidt\\
 
-  {\bfseries Received}  Month, day, year\\
-  {\bfseries Accepted}  Month, day, year\\
-  {\bfseries Published} Month, day, year\\
+  {\bfseries Received}  January 26, 2018\\
+  {\bfseries Accepted}  April 23 2018\\
+  {\bfseries Published} May 12, 2018\\
 
@@
     \bfseries\normalsize
-      \href{http://github.com/rescience/rescience-submission/article}{\faGithubAlt~Article repository}
+      \href{https://github.com/ReScience-Archives/Caze-Stimberg-Girard-2018/tree/master/article}{\faGithubAlt~Article repository}
   \end{repobox}
@@
     \bfseries\normalsize
-      \href{http://github.com/rescience/rescience-submission/code}{\faGithubAlt~Code repository}
+      \href{https://github.com/ReScience-Archives/Caze-Stimberg-Girard-2018/tree/master/code}{\faGithubAlt~Code repository}
   \end{repobox}
@@
 \begin{cases}
-    x              & \text{, if } x\leq V_a\\
-    V_a + \frac{V_c-V_a}{V_b-V_a} (x - V_a), & \text{, if } V_a<x \leq V_b\\
-    V_c            & \text{, otherwise.}
+    x,              & \text{ if } x\leq V_a,\\
+    V_a + \frac{V_c-V_a}{V_b-V_a} (x - V_a), & \text{ if } V_a<x \leq V_b,\\
+    V_c,            & \text{ otherwise.}
 \end{cases}
@@
 If they are even higher and cross the threshold $V_b$, they stop increasing the somatic voltage and saturate.
-Note that this non-linearity only affects spikes received synchronously as has been observed experimentally.
+Note that this non-linearity only affects spikes received synchronously as has been observed experimentally \cite{Softky1994}.
 With the introduction of this non-linearity, the modelled point neuron becomes an effective model of a neuron with one non-linear dendrite.
@@
 
-The parameter values used in the original study as well as in our replication are summarized in Table~\ref{tab:parameters}.
+The parameter values used in the original study as well as in our replication are summarised in Table~\ref{tab:parameters}.
 
@@
 
-We used a the predefined \verb|clip| function to implemented non-linear coupling into a network. The function clips a value to a given range, following the syntax
+We used the predefined \verb|clip| function to implement non-linear coupling in the network. The function clips a value to a given range, following the syntax
 \begin{code}
@@
 
-We employed this functions on the received excitatory inputs stored in a placed holder variable \verb|ve|.
-The variable corresponds to x in eq.~\ref{eq:non-linear}.
+We employed this function on the received excitatory inputs stored in a placed holder variable \verb|ve|.
+The variable corresponds to $x$ in eq.~\ref{eq:non-linear}.
 We then reset the variable \verb|ve| back to 0 to prepare for the next time step.
@@
 
-The \verb|run_regularly| operation enables that to run the non-linear summation between every time steps.
+The \verb|run_regularly| operation applies the non-linearity to the summed input at every time step.
 
@@
 For the grid search presented in Fig.~\ref{fig:grid}, we varied inhibitory and excitatory synaptic weights between \SI{0.16}{\milli\volt} and \SI{0.4}{\milli\volt}.
-Given that each neuron receives on average 150 excitatory and 150 inhibitory inputs, this corresponds to a ``total weight'' between \SI{24}{\milli\volt} and \SI{60}{\milli\volt}, as used on the axes of Fig.~\ref{fig:grid}).
+Given that each neuron receives on average 150 excitatory and 150 inhibitory inputs, this corresponds to a ``total weight'' between \SI{24}{\milli\volt} and \SI{60}{\milli\volt}, as used on the axes of Fig.~\ref{fig:grid}.
 We used a resolution of 100 steps for each variable, comparable to the 96 steps used in the original publication.
@@
 Both networks are simulated with the same random seed and therefore have the same network connectivity and the same initial conditions; the only difference lies in the presence or absence of external synchronous stimulation.
-Note that the correction for $g'_1$ slightly ``overcorrects'', as it discards all spikes that are resulting from background activity, even those that also would have been triggered by the stimulation.
+Note that the correction for $\hat{g}'_1$ slightly ``overcorrects'', as it discards all spikes that are resulting from background activity, even those that also would have been triggered by the stimulation.
 
@@
 Finally, we need to sum these probabilities up over all possible values for $n_\text{ex}$ and $n_\text{in}$, multiplying it with the probability that the generated input elicits a spike.
-This yiels the total probability $P^s(g_i)$ that a neuron $j$ spikes in response to the activity of $g_i$ neurons in the previous iteration:
+This yields the total probability $P^s(g_i)$ that a neuron $j$ spikes in response to the activity of $g_i$ neurons in the previous iteration:
 \begin{equation}
@@
 \textbf{Propagation of synchronous spiking in linearly (A) and non-linearly (B) coupled networks.} We initiate a chain of synchronous pulses by applying external supra-threshold inputs to the first 100 neurons at time $t=\SI{150}{\milli\second}$ (red coloured spikes, grey vertical dotted lines indicate times where spikes occur as part of the chain).
-Top row: total size $g'$ of synchronized groups within the chain.
+Top row: total size $g'$ of synchronised groups within the chain.
 Middle row: network rate over all neurons (rate in \si{\kilo\hertz}, bin size \SI{1}{\milli\second}).
@@
 For quantitative definitions, see Table~\ref{tab:color}.
-We run each combination of connection strengths 10 times, and combine the results to yield a color in RGB notation (values between 0 and 1 for the red, green, and blue component), according to:
+We run each combination of connection strengths 10 times, and combine the results to yield a colour in RGB notation (values between 0 and 1 for the red, green, and blue component), according to:
 \begin{equation}
@@
 colouring according to the class that occurred the most often, leads to visually similar results (Fig.~\ref{fig:grid_max}).
-
-\begin{table}
-\begin{tabular}{ c  l  p{0.32\textwidth}}
-  \toprule
-   & Class & Definition \\
-  \midrule
-  $U_1$ (red) & Unstable before stimulation & $\exists t<t_\text{stim}: a_b(t) \geq 100$ \\
-  $U_2$ (yellow) & Unstable after stimulation & $\exists t>t_\text{stim}: a_b(t) \geq 100$ \\
-  $E$ (green) &  Stable activity, no propagation & $\forall t: a_b(t) < 100\, \wedge\, g_\text{p} < 10$\\
-  $S$ (blue) & Stable activity, persistent propagation & $\forall t: a_b(t) < 100\, \wedge\, g_\text{p} \geq 10$\\
-  \bottomrule
-\end{tabular}
-\caption{Classification of network behaviour for Fig.~\ref{fig:grid}.
-Here, $a_b$ refers to the background activity, the number of neurons active during a \SI{1}{\milli\second} time bin, ignoring the time steps at $t_\text{p}^k = t_\text{stim} + k\cdot\tau$, i.e.
-time steps that follow the synchronous stimulation by multiples of the synaptic delay.
-The variable $g_\text{p}$ refers to the number of successful propagations of the synchronous activity, i.e.
-the number of time steps $t_\text{p}^k$ where the number of active neurons exceeds the maximal background activity $a_b$.}\label{tab:color}
-\end{table}
-
-Our replication does not reproduce all the quantitative details of the original plots.
-The parameter range where simulations are only unstable after they receive the synchronous stimulation (yellow) is smaller than in the original article.
-For linear networks, we do observe almost no simulations classified in this category, while the original article has a thin line of such classifications between the stable regime without propagation (green) and the regime where simulations are unstable even without stimulation (red).
-Similarly, in the original article the parameter exploration shows for each inhibitory connection weight a range of excitatory connection weights of about \SI{5}{\milli\volt} where the network is unstable only after the synchronous stimulation (yellow).
-In contrast, our simulations show a much smaller zone when the inhibitory connection strength is small (Fig.~\ref{fig:grid}B).
-It seems that these differences mostly stem from the fact that the transition to the regime where simulations are unstable without stimulation (red) happens for lower excitatory and higher inhibitory connection strength in our simulations than in the original article, i.e.
-that the red zone is shifted towards the bottom left.
-This is particularly evident for strong excitatory and inhibitory connections in non-linearly coupled networks (bottom right in Fig.~\ref{fig:grid}B and C) which are unstable in our simulations, but stable or only unstable after stimulation in the original publication.
-Simulating the parameter combination corresponding to the point in the bottom right corner of the plot different time resolutions (Fig.~\ref{fig:raster_strong}), we find that this difference does indeed seem to be triggered by limited time resolution in the model.
-The forced synchronisation of all spikes to a grid of \SI{0.1}{\milli\second}, together with the homogeneity of the synaptic delays, leads to strong oscillations in our simulation (Fig.~\ref{fig:raster_strong}A), which is consequently classified as unstable.
-When we use a simulation time step of \SI{0.01}{\milli\second}, these osciallations disappear and the network activity therefore gets classified as ``stable without persistent propagation''.
-Finally, non-linearly coupled networks show a discontinuity for weak inhibitory connection strengths in the original publication.
-For increasing excitatory connection strengths, network behaviour goes from stable (blue) to unstable after stimulation (yellow) to unstable before stimulation (red), but then get classified again as stable (blue) in a small range of parameters before finally transitioning to unstable activity (yellow and red).
-We do not observe this in our simulations, but simulations with a finer time resolution (Fig.~\ref{fig:grid_detail}C) indicate that this difference could be caused by the limited time resolution of our simulations as well.
-
-Despite these differences, the qualitative network behaviour looks very similar on a coarse scale.
-Importantly, it strongly supports the original paper's main conclusion that non-linearly coupled networks have a large parameter range of stable propagation (i.e., blue-coloured points), while linearly coupled networks do not.
-The differences in our replication are most likely due to our use of a clock-based simulation method with a limited time resolution (see Fig.~\ref{fig:grid_detail} and Fig.~\ref{fig:raster_strong}).
-In principle, another reason could be implementation details of the initial ``spikes in transit'' that were not fully specified in the original article, but this seems unlikely since completely removing them did not change the results in a noticeable way (not shown).
 
@@
 \end{figure}
+
+\begin{table}
+\begin{tabular}{ c  l  p{0.32\textwidth}}
+  \toprule
+   & Class & Definition \\
+  \midrule
+  $U_1$ (red) & Unstable before stimulation & $\exists t<t_\text{stim}: a_b(t) \geq 100$ \\
+  $U_2$ (yellow) & Unstable after stimulation & $\exists t>t_\text{stim}: a_b(t) \geq 100$ \\
+  $E$ (green) &  Stable activity, no propagation & $\forall t: a_b(t) < 100\, \wedge\, g_\text{p} < 10$\\
+  $S$ (blue) & Stable activity, persistent propagation & $\forall t: a_b(t) < 100\, \wedge\, g_\text{p} \geq 10$\\
+  \bottomrule
+\end{tabular}
+\caption{Classification of network behaviour for Fig.~\ref{fig:grid}.
+Here, $a_b$ refers to the background activity, the number of neurons active during a \SI{1}{\milli\second} time bin, ignoring the time steps at $t_\text{p}^k = t_\text{stim} + k\cdot\tau$, i.e.
+time steps that follow the synchronous stimulation by multiples of the synaptic delay.
+The variable $g_\text{p}$ refers to the number of successful propagations of the synchronous activity, i.e.
+the number of time steps $t_\text{p}^k$ where the number of active neurons exceeds the maximal background activity $a_b$.}\label{tab:color}
+\end{table}
+
+Our replication does not reproduce all quantitative details of the original plots.
+For non-linearly coupled networks, the parameter range where simulations are only unstable after they receive the synchronous stimulation (yellow) is smaller than in the original article.
+The original article shows for each inhibitory connection weight a range of excitatory connection weights of about \SI{5}{\milli\volt} with such a behaviour.
+In contrast, our simulations show a much smaller such zone when the inhibitory connection strength is small (Fig.~\ref{fig:grid}B).
+It seems that these differences mostly stem from the fact that the transition to the regime where simulations are unstable without stimulation (red) happens for lower excitatory and higher inhibitory connection strength in our simulations than in the original article, i.e.
+that the red zone is shifted towards the bottom left.
+This is particularly evident for strong excitatory and inhibitory connections in non-linearly coupled networks (bottom right in Fig.~\ref{fig:grid}B and C) which are unstable in our simulations, but stable or only unstable after stimulation in the original publication.
+Simulating the parameter combination corresponding to the point in the bottom right corner of the plot at different time resolutions (Fig.~\ref{fig:raster_strong}), we find that this difference does indeed seem to be triggered by limited time resolution in the model.
+The forced synchronisation of all spikes to a grid of \SI{0.1}{\milli\second}, together with the homogeneity of the synaptic delays, leads to strong oscillations in our simulation (Fig.~\ref{fig:raster_strong}A), which is consequently classified as unstable.
+When we use a simulation time step of \SI{0.01}{\milli\second}, these oscillations disappear and the network activity therefore gets classified as ``stable without persistent propagation''.
+Finally, non-linearly coupled networks show a discontinuity for weak inhibitory connection strengths in the original publication.
+For increasing excitatory connection strengths, network behaviour goes from stable (blue) to unstable after stimulation (yellow) to unstable before stimulation (red), but then get classified again as stable (blue) in a small range of parameters before finally transitioning to unstable activity (yellow and red).
+We do not observe this in our simulations, but simulations with a finer time resolution (Fig.~\ref{fig:grid_detail}C) indicate that this difference could be caused by the limited time resolution of our simulations as well.
+
+Despite these differences, the qualitative network behaviour looks very similar on a coarse scale.
+Importantly, it strongly supports the original paper's main conclusion that non-linearly coupled networks have a large parameter range of stable propagation (i.e., blue-coloured points), while linearly coupled networks do not.
+The differences in our replication are most likely due to our use of a clock-based simulation method with a limited time resolution (see Fig.~\ref{fig:grid_detail} and Fig.~\ref{fig:raster_strong}).
+In principle, another reason could be implementation details of the initial ``spikes in transit'' that were not fully specified in the original article, but this seems unlikely since completely removing them did not change the results in a noticeable way (not shown).
 
@@
 In our simulation, the semi-analytical solution overestimates the numerical one.
-Be reminded that to obtain this good quantitative match, we however had to apply a correction to the numerical results, as explained in the implementation section (for the uncorrected values, see Fig.~\ref{fig:markov}).
+Be reminded that to obtain this good quantitative match, we had to apply a correction to the numerical results, as explained in the implementation section (for the uncorrected values, see Fig.~\ref{fig:markov}).
 
-Despite the small quantitative differences, our work strengthens the original result demonstrating a qualitative difference between linearly coupled and non-linearly coupled networks.
+Despite the small quantitative differences, our work strengthens the original result by demonstrating a qualitative difference between linearly coupled and non-linearly coupled networks.
 
@@
 
-We managed to qualitatively reproduce the main results of Raoul-Martin Memmes\-heimer and Marc Timme \cite{Memmesheimer2012} despite some slight quantitative differences.
+We managed to qualitatively reproduce the main results of Raoul-Martin Memmes\-heimer and Marc Timme \cite{Memmesheimer2012} despite some quantitative differences.
 The grid search over parameters showed a higher prevalence of networks with unstable activity before the onset of stimulation compared to the original study.
-In the analysis of the evolution of synchronous pulses of different sizes, our results need a correction for the use of a clock-based simulation method to show a good quantative match with the original results.
+In the analysis of the evolution of synchronous pulses of different sizes, our results need a correction for the use of a clock-based simulation method to show a good quantitative match with the original results.
 However, a marked difference remains for small initial group sizes.
-The differences we see are most likely due to our use of a clock-based instead of event-driven simulations, as it forces all activity to a temporal grid of finite precision.
+The differences we see are most likely due to our use of clock-based instead of event-driven simulations, as it forces all activity to a temporal grid of finite precision.
 However, the main qualitative finding---non-linearly coupled networks have a large parameter range supporting persistent propagation of synchronous activity whereas linearly coupled networks do not---remains if we use finer (\SI{0.05}{\milli\second}) or coarser (\SI{0.2}{\milli\second}, \SI{0.5}{\milli\second}) temporal resolutions (data not shown).
@@
 \caption{\label{fig:grid_max}
-\textbf{Using max instead of mean to color each pixels.} All conventions as in Fig.~\ref{fig:grid}, but points are coloured according the observed qualitative behaviour that occurred the most often among the 10 independent simulations for given connection strengths.}
+\textbf{Most-often observed qualitative network behaviour as a function of excitatory and inhibitory connection
+strength} All conventions as in Fig.~\ref{fig:grid}, but points are coloured according the observed qualitative behaviour that occurred the most often among the 10 independent simulations for given connection strengths.}
 \end{figure}
@@
 \caption{\label{fig:grid_detail}
-\textbf{Zoom on qualitative network behaviour with different simulation time steps.} Color code as in Fig.~\ref{fig:grid}.
+\textbf{Zoom on qualitative network behaviour with different simulation time steps.} Colour code as in Fig.~\ref{fig:grid}.
 Results are shown for a smaller range of connection strengths than in Fig.~\ref{fig:grid}, and only for non-linearly coupled networks with an synchronous stimulation of 100 neurons.
@@
 \caption{\label{fig:raster_strong}
-\textbf{Propagation of synchronous spiking when simulated with small timesteps}.(A) Time step of \SI{0.1}{\milli\second}, or \SI{0.01}{\milli\second} (B) All conventions as in Fig.~\ref{fig:raster}, but for strong recurrent connections ($w_\text{ex} = w_\text{in} = \SI{0.4}{\milli\volt}$).
+\textbf{Propagation of synchronous spiking in strongly connected networks when simulated with a time step of \SI{0.1}{\milli\second} (A), or \SI{0.01}{\milli\second} (B)}.
+All conventions as in Fig.~\ref{fig:raster}, but for strong recurrent connections ($w_\text{ex} = w_\text{in} = \SI{0.4}{\milli\volt}$).
 Both simulated networks use non-linearly coupling, the network shown in panel (B) is simulated with a 10-times finer temporal resolution compared to the other results shown.}
@@
 \textbf{Evolution of synchronous pulses without correction in linearly (A) and non-linearly (B) coupled networks.} All conventions as in Fig.~\ref{fig:markov_corrected}.
-The numerical results shown here (gray lines and green squares) are not corrected for the bias introduced by the clock-driven integration method (see text for details).}
+The numerical results shown here (grey lines and green squares) are not corrected for the bias introduced by the clock-driven integration method (see text for details).}
 \end{figure}
